### 2024-02-12 outputs/paper/paper.qmd
update paper structure

---
title: "Echoes of Economic Downturn: Investigating the Persistent Impact of the Great Recession on Birth Rates Among Young Americans"
author: 
  - Yuanyi (Leo) Liu
  - Emma Teng
thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-s-Impact-on-Young-Americans-Birth-Rates/tree/main. A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802"
date: today
date-format: long
abstract: "In our study, we delve into the trend of declining US birth rates among young individuals, particularly in light of the Great Recession's aftermath. By examining similar demographic and cohort factors as Kearney et al. (2022), we extend the investigation to include the potential influences of the feminist movement and advancements in technology and media. Our findings align with Kearney et al., reinforcing the notion of changing priorities among younger generations. This replication highlights the complex interplay of societal shifts and economic conditions on fertility decisions, offering a nuanced understanding of contemporary demographic trends."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

# install.packages("knitr")
# install.packages("opendatatoronto")
# install.packages("tidyverse")
# install.packages("here")
# install.packages("tidyr")
# install.packages("dplyr")
# install.packages("kableExtra")

# library(knitr)
# library(opendatatoronto)
# library(tidyverse)
# library(here)
# library(tidyr)
# library(dplyr)
# library(kableExtra)
# library(janitor)
```

# Introduction {#sec-intro}

The paper is structured to facilitate a comprehensive understanding of the study and its implications. Following @sec-intro, @sec-data presents the data, detailing the data sources, analytical techniques, and the rationale behind the chosen methods. @sec-result discusses the results, elaborating on the observed trends and patterns in crime data. @sec-discussion provides an in-depth discussion of these findings, exploring potential factors influencing these trends, drawing connections to broader urban issues, and providing suggestions for future research in this area.

\newpage

# Data {#sec-data}

This section aims to offer an insightful understanding of the dataset utilized in our analysis, focusing on its content, origin, and the methods applied for data manipulation and visualization.

## Source

Although alternative datasets were considered, this specific dataset was selected for its detailed year-wise breakdown and the diversity of crime types it encompasses. Other datasets either lacked the temporal detail or the variety of crime categories present in our chosen dataset.

## Methodology
The data was processed and cleaned using R[@citeR], a powerful statistical programming language. For key operations, please refer to the [@sec-appendix].

## Variables
To better understand the data, the summary_table dataset was developed to offer a more structured and aggregated view of the crime data. By transforming and summarizing the data into a format that displays crime types against years, this dataset simplifies the task of identifying and analyzing trends over time. The dataset includes various crime categories, such as assault, theft, and other types, with each variable representing the annual count of reported cases for each crime type. This longitudinal data provides a detailed view of the crime trends in Toronto over a decade. 
```{r}

```

We proceeded to organize the dataset into two categories: 'Violent' crimes, which included offenses such as 'Assault' and 'Homicide', and 'Non-Violent' crimes, encompassing acts like 'Theft'. It is particularly valuable for understanding the overall landscape of crime in Toronto, focusing on the comparison between violent and non-violent incidents.
```{r}

```

## Measurements

\newpage

# Results {#sec-result}
In this section, we delve into the core findings of our study, shedding light on the intricate patterns and trends of crime in Toronto from 2014 to 2023. Our analysis dissects both violent and non-violent crime statistics, revealing insightful correlations and variations over the decade.
```{r fig.width=10, fig.height=5.5}

```

```{r}

```
\newpage

The red line represents violent crimes, and the blue line represents non-violent crimes. The plot shows distinct trends for both categories over the specified time frame.

* **Violent Crimes (Red Line):** There has been an overall increasing trend in the number of violent crime cases over the years. There are some fluctuations, with a noticeable dip occurring in one of the years, but the general direction is upwards, especially towards the end of the period, indicating a rise in violent crimes or an increase in reporting.

* **Non-Violent Crimes (Blue Line):** The trend in non-violent crime cases shows some variability but does not have as clear an increasing pattern as violent crimes. There are years where the rate has increased or decreased, but the last year shows a notable increase, suggesting a possible upward trend at the end of the period.

Overall, the graph indicates that while both violent and non-violent crimes have seen rises and falls, the increase in violent crimes towards the later years is more pronounced. This could reflect changes in societal conditions, law enforcement practices, or reporting mechanisms.

\newpage

# Discussion {#sec-discussion}

The analysis of Toronto's crime trends from 2014 to 2023 reveals a complex and evolving landscape of public safety. The pronounced increase in assault cases in recent years is alarming, suggesting that the city may be facing emerging challenges in maintaining public order. This rise in violent crime needs a closer investigation of possible causative factors, such as the effects of increased urbanization, economic disparity, and shifts in population density.

## Variation in Crime Trends {#sec-first-point}

Simultaneously, the decline in theft-related crimes offers a more hopeful narrative. This trend may reflect the successful implementation of preventative measures by law enforcement agencies, such as community policing efforts and the integration of advanced surveillance technology. The use of crime prevention techniques, potentially aided by increased public awareness and education, appears to be bearing fruit.

The contrast between the trajectories of violent and non-violent crime rates underscores the need for a differentiated approach to policy-making and law enforcement. While we appreciate our gains in decreasing property crimes, the data motivates us to pursue more effective interventions for preventing and reacting to violent crimes. This might include extending social services, improving community engagement, and investing in data-driven police strategies.

## Weaknesses and Next Steps

While the visualization provides a high-level overview of crime trends in Toronto, it's essential to conduct a more detailed analysis to understand the underlying causes of these trends. This includes examining subcategories of crimes, focusing on specific geographic areas within the city, and considering other relevant data sources.

Furthermore, this study emphasises the need for ongoing monitoring and analysis of crime data to comprehend the ever-changing dynamics of urban crime. In light of these findings, future studies should focus on understanding the influence of specific policies and social changes on crime rates. Only by doing such a comprehensive analysis can we hope to develop strategies that will ensure the safety and well-being of all Toronto residents.

\newpage

# References

::: {#refs}
:::

{{< pagebreak >}}

# Appendix {#sec-appendix}
## Data Manipulation and Cleaning
* **Data Cleaning:** The initial phase of cleaning the Toronto crime rates dataset involved importing the raw data using the `read_csv` function from the `readr`[@citereadr] package. Following the import, the dataset was streamlined using the `select` function from `dplyr`[@citedplyr], a tidyverse[@citetidyverse] package, to remove irrelevant columns such as `X_id`, `HOOD_ID`, `POPULATION_2023`, and `geometry`. This step was crucial to focus the analysis on relevant variables. Additionally, the `na.omit` function was employed to discard any rows with missing values (NA), ensuring the dataset's completeness and reliability. The final step in the cleaning process was the exportation of the cleaned data into a new CSV file using the `write_csv `function from `readr`[@citereadr], thereby preserving the cleaned and refined dataset for subsequent analysis.

* **Data Transformation:** The dataset was transformed from a wide format to a long format using the `gather` function from the `tidyr`[@citetidyr] package. This transformation is crucial for simplifying the data structure and making it more amenable to analysis. Also, the separate function, again from `tidyr`[@citetidyr], was instrumental in dividing the 'Crime_Year' column into two distinct parts: 'Crime_Type' and 'Year'. This enhances the granularity of the dataset, allowing for more detailed analysis.

* **Aggregation:** The `group_by` and `summarise` functions from `dplyr`[@citedplyr] were employed to aggregate the data by year and crime type.

* **Data Visualization:** For visual representation, `ggplot2`[@citeggplot], a versatile package in R for data visualization, was employed. It was used to create comprehensive line plots depicting the trends of various crime categories over the years.

* **Paper Generation:** The packages `knitr`[@citeknitr] is used in generating R Markdown reports.

### 2024-02-12 scripts/00-simulate_data.R

@@ -1,0 +1,38 @@
+#### Preamble ####
+# Purpose: Simulates data
+# Author: Yuanyi (Leo) Liu
+# Email: leoy.liu@mail.utoronto.ca
+# Date: 21 January 2024
+# License: MIT
+
+
+#### Workspace setup ####
+# install.packages("janitor")
+# install.packages("tidyverse")
+library(janitor)
+library(tidyverse)
+
+
+#### Simulate ####
+
+# In this simulation, we only want the number of cases reported of each crime type from 2014 to 2023.
+# First, A tibble is created with initial Crime_Type column.
+# Second, A loop runs through each year from 2014 to 2023.
+# In each iteration of the loop, a new column is added to simulated_data for the respective year. 
+# The sample function generates random counts for the crimes for that year.
+# Third, replace = TRUE in the sample function allows for the possibility of the same number being chosen more than once.
+
+set.seed(853)
+
+crime_types <- c("Assault", "Auto Theft", "Bike Theft", "Break and Enter", "Homicide", "Robbery", "Shooting Incidents", "Theft from Motor Vehicles", "Major Theft")
+
+# Initialize a tibble
+simulated_data <- tibble(Crime_Type = crime_types)
+
+# Add columns for each year from 2014 to 2023 with simulated data
+for(year in 2014:2023) {
+  simulated_data[[as.character(year)]] <- sample(500:10000, length(crime_types), replace = TRUE)
+}
+
+# View the simulated data
+print(simulated_data)

### 2024-02-12 scripts/01-download_data.R

@@ -1,0 +1,31 @@
+#### Preamble ####
+# Purpose: Downloads, saves, and reads data from the OpenDataToronto portal
+# Author: Yuanyi (Leo) Liu
+# Date: 21 January 2024
+# Contact: leoy.liu@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(opendatatoronto)
+library(tidyverse)
+library(dplyr)
+
+
+#### Download data ####
+# Each package is associated with a unique id  found in the "For 
+# Developers" tab of the relevant page from Open Data Toronto
+# source: https://open.toronto.ca/dataset/neighbourhood-crime-rates/
+toronto_crime_rates <-
+  list_package_resources("neighbourhood-crime-rates") |>
+  filter(name == "neighbourhood-crime-rates - 4326.csv") |>
+  get_resource()
+
+
+#### Save data ####
+write_csv(
+  x = toronto_crime_rates,
+  file = "toronto_crime_rates.csv"
+)
+
+head(toronto_crime_rates)

### 2024-02-12 scripts/02-data_cleaning.R

@@ -1,0 +1,98 @@
+#### Preamble ####
+# Purpose: Cleans the raw plane data
+# Author: Yuanyi (Leo) Liu
+# Date: 21 January 2024
+# Contact: leoy.liu@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+
+#### Cleaned data ####
+raw_data <- read_csv("inputs/data/toronto_crime_rates.csv")
+
+# Removing unwanted columns
+cleaned_data <- raw_data %>% select(-c(X_id, HOOD_ID, POPULATION_2023, geometry))
+
+# Removing rows with NA values
+cleaned_data <- na.omit(cleaned_data)
+
+# Save data #
+write_csv(
+  x = cleaned_data,
+  file = "cleaned_toronto_crime_rates.csv"
+)
+
+# Descriptive Summaries #
+str(cleaned_data)
+summary(cleaned_data)
+
+
+
+#### Summary Table Dataset ####
+
+# Read the data
+crime_data <- read.csv(here("inputs/data/cleaned_toronto_crime_rates.csv"))
+
+# Remove unnecessary columns
+crime_data <- crime_data %>%
+  select(-grep("RATE", names(crime_data)))
+
+# Gather the data to a long format
+crime_data_long <- crime_data %>%
+  gather(key = "Crime_Year", value = "Count", -AREA_NAME)
+
+# Extract year and crime type from the 'Crime_Year' column
+crime_data_long <- crime_data_long %>%
+  separate(Crime_Year, into = c("Crime_Type", "Year"), sep = "_") %>%
+  mutate(Year = as.numeric(Year))
+
+# Aggregate the data by year and crime type
+crime_data_summary <- crime_data_long %>%
+  group_by(Crime_Type, Year) %>%
+  summarise(Total = sum(Count, na.rm = TRUE), .groups = "drop")
+
+# Creating the summary table
+summary_table <- crime_data_summary %>%
+  group_by(Crime_Type, Year) %>%
+  summarise(Total_Cases = sum(Total, na.rm = TRUE), .groups = "drop") %>%
+  spread(key = Year, value = Total_Cases)
+
+# Define a mapping for crime types
+readable_crime_types <- c('ASSAULT' = 'Assault',
+                          'AUTOTHEFT' = 'Auto Theft',
+                          'BIKETHEFT' = 'Bike Theft',
+                          'BREAKENTER' = 'Break and Enter',
[…]

### 2024-02-12 scripts/03-test_data.R

@@ -1,0 +1,70 @@
+#### Preamble ####
+# Purpose: Tests
+# Author: Yuanyi (Leo) Liu
+# Date: 24 January 2024
+# Contact: leoy.liu@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+
+#### Test data ####
+# Load dataset
+cleaned_toronto_crime_rates <- read.csv("inputs/data/cleaned_toronto_crime_rates.csv", check.names = FALSE)
+summary_table <- read.csv("inputs/data/summary_table.csv", check.names = FALSE)
+two_types_crime <- read.csv("inputs/data/two_types_crime.csv", check.names = FALSE)
+
+# Test 1: Check for missing values for cleaned_toronto_crime_rates
+test1_result <- !any(is.na(cleaned_toronto_crime_rates))
+print(paste("Test 1 Passed:", test1_result))
+
+# Test 2: Check for duplicated rows for cleaned_toronto_crime_rates
+test2_result <- !any(duplicated(cleaned_toronto_crime_rates))
+print(paste("Test 2 Passed:", test2_result))
+
+# Test 3: Check the number of columns for summary_table
+expected_num_cols <- 11
+test3_result <- ncol(summary_table) == expected_num_cols
+print(paste("Test 3 Passed:", test3_result))
+
+# Test 4: Check the number of rows for summary_table
+expected_num_rows <- 9
+test4_result <- nrow(summary_table) == expected_num_rows
+print(paste("Test 4 Passed:", test4_result))
+
+# Test 5: Check for missing values for summary_table
+test5_result <- !any(is.na(summary_table))
+print(paste("Test 5 Passed:", test5_result))
+
+# Test 6: Check for duplicated rows for summary_table
+test6_result <- !any(duplicated(summary_table))
+print(paste("Test 6 Passed:", test6_result))
+
+# Test 7: Check for positive values in year columns
+year_columns <- c('2014', '2015', '2016', '2017', '2018', '2019', '2020', '2021', '2022', '2023')
+test7_result <- all(sapply(summary_table[year_columns], function(x) all(x >= 0)))
+print(paste("Test 7 Passed:", test7_result))
+
+# Test 8: Check column types for summary_table
+test8_result <- is.character(summary_table$Crime_Type)
+print(paste("Test 8 Passed:", test8_result))
+
+# Test 9: Check the number of columns for two_types_crime
+expected_num_cols <- 11
[…]

### 2024-02-13 outputs/paper/paper.qmd
Initial Update for the paper

@@
 date-format: long
-abstract: "In our study, we delve into the trend of declining US birth rates among young individuals, particularly in light of the Great Recession's aftermath.
-By examining similar demographic and cohort factors as Kearney et al.
-(2022), we extend the investigation to include the potential influences of the feminist movement and advancements in technology and media.
-Our findings align with Kearney et al., reinforcing the notion of changing priorities among younger generations.
-This replication highlights the complex interplay of societal shifts and economic conditions on fertility decisions, offering a nuanced understanding of contemporary demographic trends."
+abstract: "In this study, we explore the impact of the Great Recession on birth rates among young people in the United States, utilizing a comprehensive analysis of demographic and economic data.
+Our findings reveal a significant decline in birth rates within this group during and following the economic downturn, highlighting the intricate relationship between economic stability and reproductive decisions.
+This research contributes to our understanding of how macroeconomic factors can have profound effects on personal life choices, emphasizing the need for supportive policies targeting young individuals during economic crises."
 format: pdf
@@
 
-# install.packages("knitr")
-# install.packages("opendatatoronto")
-# install.packages("tidyverse")
-# install.packages("here")
-# install.packages("tidyr")
-# install.packages("dplyr")
-# install.packages("kableExtra")
+install.packages("knitr")
+install.packages("opendatatoronto")
+install.packages("tidyverse")
+install.packages("here")
+install.packages("tidyr")
+install.packages("dplyr")
+install.packages("kableExtra")
 
-# library(knitr)
-# library(opendatatoronto)
-# library(tidyverse)
-# library(here)
-# library(tidyr)
-# library(dplyr)
-# library(kableExtra)
+library(knitr)
+library(opendatatoronto)
+library(tidyverse)
+library(here)
+library(tidyr)
+library(dplyr)
+library(kableExtra)
 # library(janitor)
@@
 
+The Great Recession, a defining economic event of the early 21st century, has been subject to extensive analysis for its profound effects on employment, housing, and financial systems globally.
+However, its impact on demographic trends, particularly birth rates among young people in the United States, has not been thoroughly explored.
+This paper aims to fill this gap by examining how the economic downturn influenced reproductive decisions among this demographic.
+
+Utilizing a blend of quantitative data analysis and demographic research, we investigated birth rate trends among young adults during and following the recessionary period.
+Our methodology involved analyzing birth rate data in conjunction with economic indicators such as unemployment rates, income levels, and housing market trends to draw correlations and insights.
+
+Our findings reveal a significant decline in birth rates among young Americans during the recession, with lingering effects in the subsequent years.
+This trend suggests that economic instability has a profound impact on personal life choices, including the decision to have children.
+The implications of these findings are far-reaching, affecting not only demographic forecasting but also social policy and economic recovery strategies.
+
 The paper is structured to facilitate a comprehensive understanding of the study and its implications.
 Following @sec-intro, @sec-data presents the data, detailing the data sources, analytical techniques, and the rationale behind the chosen methods.
-@sec-result discusses the results, elaborating on the observed trends and patterns in crime data.
-@sec-discussion provides an in-depth discussion of these findings, exploring potential factors influencing these trends, drawing connections to broader urban issues, and providing suggestions for future research in this area.
+@sec-result discusses the results, elaborating on the observed trends and patterns in brth rate data.
+@sec-discussion provides an in-depth discussion of these findings, exploring potential factors influencing these trends, drawing connections to broader socio-economic issues, and providing suggestions for future research in this area.
 
@@
 This longitudinal data provides a detailed view of the crime trends in Toronto over a decade.
+
+TODO: Add a table here to better understand the data.
+
 ```{r}
 
+ggplot(figure,
+        aes(x = year, y = brate_all)) + 
+        geom_line(color="red") +
+        geom_vline(xintercept = 2007, color = "black", linetype = "dashed") +
+        annotate("text", x = 2007, y = 60, label = "Global Financial Crisis of 2007-2008", 
+                 color = "black", angle = 90, vjust = -0.5) +
+        labs(title = "Birth Rate in America overtime",
+            x = "Years",
+            y = "Birth rate") +
+        theme(panel.background = element_rect(fill = "white"),
+              plot.background = element_rect(fill = "white", color = NA),
+              plot.title = element_text(color = "black", size = 14, face = "bold"),
+              axis.title = element_text(color = "black"))
 ```
-
-We proceeded to organize the dataset into two categories: 'Violent' crimes, which included offenses such as 'Assault' and 'Homicide', and 'Non-Violent' crimes, encompassing acts like 'Theft'.
-It is particularly valuable for understanding the overall landscape of crime in Toronto, focusing on the comparison between violent and non-violent incidents.
-```{r}
-
-```
+// TODO: Visualization of the data for intuition
 
 ## Measurements
+
+// TODO: Add a summary table to show measurements
 
@@
 Our analysis dissects both violent and non-violent crime statistics, revealing insightful correlations and variations over the decade.
-```{r fig.width=10, fig.height=5.5}
-
-```
 
 ```{r}
+ggplot(cleaned_data, aes(x = year, y = brate, color = age_group)) +
+  geom_line(size=1) +
+  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") + 
+  annotate("text", x = 2007, y = 60, label = "2007", 
+           color = "black", angle = 90, vjust = -0.5) +
+  labs(title = "Birth Rate by Age Group Over Time",
+       x = "Year",
+       y = "Birth Rate") +
+  theme(panel.background = element_rect(fill = "white"),
+        plot.background = element_rect(fill = "white", color = NA),
+        plot.title = element_text(color = "black", size = 14, face = "bold"),
+        axis.title = element_text(color = "black"))
+```
+// TODO: Explain the figure
 
+// TODO: Transit to following figure
+```{r fig.width=10, fig.height=5.5}
+ggplot(merged_data, aes(x = long, y = lat, group=group)) +
+  geom_polygon(aes(fill = brate1544_thsnds_ch_pct)) +
+  scale_fill_gradient(low = 'darkred', high = '#FFCCCB') +
+  labs(title = 'Change in Birth Rate by State Over Time',
+       fill = 'Change in Birth Rate') +
+  theme_void()
 ```
-\newpage
-
-The red line represents violent crimes, and the blue line represents non-violent crimes. The plot shows distinct trends for both categories over the specified time frame.
-
-* **Violent Crimes (Red Line):** There has been an overall increasing trend in the number of violent crime cases over the years.
-There are some fluctuations, with a noticeable dip occurring in one of the years, but the general direction is upwards, especially towards the end of the period, indicating a rise in violent crimes or an increase in reporting.
-
-* **Non-Violent Crimes (Blue Line):** The trend in non-violent crime cases shows some variability but does not have as clear an increasing pattern as violent crimes.
-There are years where the rate has increased or decreased, but the last year shows a notable increase, suggesting a possible upward trend at the end of the period.
-
-Overall, the graph indicates that while both violent and non-violent crimes have seen rises and falls, the increase in violent crimes towards the later years is more pronounced.
-This could reflect changes in societal conditions, law enforcement practices, or reporting mechanisms.
+// TODO: Explain the figure
 
@@
 
-## Variation in Crime Trends {#sec-first-point}
+## Findings
 
@@
 
+## Economic Impact Insights
+
 The contrast between the trajectories of violent and non-violent crime rates underscores the need for a differentiated approach to policy-making and law enforcement.
@@
 
-## Weaknesses and Next Steps
+## Societal and Technological Influences
+
+// TODO
+
+## Weaknesses
 
@@
 This includes examining subcategories of crimes, focusing on specific geographic areas within the city, and considering other relevant data sources.
+
+## Future Research Directions
 

### 2024-02-13 scripts/fig_1.R

@@ -1,0 +1,13 @@
+#Workspace set up
+
+library(tidyverse)
+library(dplyr)
+library(here)
+library(ggplot2)
+
+figure <- read.csv(here::here("inputs/data/fig_1.csv"))
+
+write_csv(
+  x = figure,
+  file = "outputs/data/figure_1.csv"
+)

### 2024-02-13 scripts/fig_2.R

@@ -1,0 +1,30 @@
+library(dplyr)
+library(tidyverse)
+library(here)
+library(ggplot2)
+
+uncleaned_data <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
+
+cleaned_data <- uncleaned_data |>
+  select(brate_1519, brate_2024, brate_2529, brate_3034, brate_3539, brate_4044, year)
+
+cleaned_data <- cleaned_data |>
+  rename(
+    "br_15 to 19" = brate_1519,
+    "br_20 to 24" = brate_2024,
+    "br_25 to 29" = brate_2529,
+    "br_30 to 34" = brate_3034,
+    "br_35 to 39" = brate_3539,
+    "br_40 to 44" = brate_4044,
+  )
+
+cleaned_data <- cleaned_data |>
+  pivot_longer(cols = starts_with("br_"),
+               names_to = "age_group",
+               names_prefix = "br_",
+               values_to = "brate")
+
+write_csv(
+  x = cleaned_data,
+  file = "outputs/data/figure_2.csv"
+)

### 2024-02-13 scripts/fig_3a.R

@@ -1,0 +1,39 @@
+library(tidyverse)
+library(dplyr)
+library(sf)
+library(here)
+library(ggplot2)
+library(mapdata)
+library(haven)
+
+uncleaned_data <- read.csv(here::here("inputs/data/fig_3.csv"))
+
+state <- map_data("state")
+
+#data <- read_dta(here::here('data/nchs/nchs_births_pop_1990_2019.dta'))
+
+cleaned_data <- uncleaned_data [-c(1, 12), ]
+
+state_full <- tibble(
+  stname=cleaned_data$stname,
+  full=c("alabama", "arkansas", "arizona", "california", "colorado", "connecticut", "district of columbia", "delaware",
+         "florida", "georgia", "iowa", "idaho", "illinois", "indiana", "kansas", "kentucky", "louisiana", "massachusetts", "maryland", "maine", "michigan",
+         "minnesota", "missouri", "mississippi", "montana", "north carolina", "north dakota", "nebraska", "new hampshire", "new jersey", "new mexico",
+         "nevada", "new york", "ohio", "oklahoma", "oregon", "pennsylvania", "rhode island", "south carolina", "south dakota",
+         "tennessee", "texas", "utah", "virginia", "vermont", "washington", "wisconsin","west virginia", "wyoming"
+         )
+)
+
+
+cleaned_data <- cleaned_data |>
+  left_join(state_full, by = "stname") |>
+  select(-stname) |>
+  rename(stname = full)
+
+
+merged_data <- merge(state, cleaned_data, by.x = "region", by.y = "stname", all.x = TRUE)
+
+write_csv(
+  x = merged_data,
+  file = "outputs/data/figure_3a.csv"
+)

### 2024-02-13 outputs/paper/paper.qmd
Deleted unnecessary dataset, fixed git by reclone, fixed figure display in qmd file. Tables to be implemented.

@@
   - Yuanyi (Leo) Liu
-  - Emma Teng
+  - Qi Er (Emma) Teng
 thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-s-Impact-on-Young-Americans-Birth-Rates/tree/main.
@@
 
-install.packages("knitr")
-install.packages("opendatatoronto")
-install.packages("tidyverse")
-install.packages("here")
-install.packages("tidyr")
-install.packages("dplyr")
-install.packages("kableExtra")
-
-library(knitr)
-library(opendatatoronto)
 library(tidyverse)
+library(dplyr)
 library(here)
-library(tidyr)
-library(dplyr)
-library(kableExtra)
-# library(janitor)
+library(mapdata)
+library(ggplot2)
+library(haven)
 ```
@@
 TODO: Add a table here to better understand the data.
+```{r}
+```
 
+// Visualization of the data for intuition
 ```{r}
 
-ggplot(figure,
+figure1 <- read.csv(here::here("outputs/data/figure_1.csv"))
+
+ggplot(figure1,
         aes(x = year, y = brate_all)) + 
@@
 ```
-// TODO: Visualization of the data for intuition
 
@@
 ```{r}
-ggplot(cleaned_data, aes(x = year, y = brate, color = age_group)) +
+figure2 <- read.csv(here::here("outputs/data/figure_2.csv"))
+
+ggplot(figure2, aes(x = year, y = brate, color = age_group)) +
   geom_line(size=1) +
@@
 // TODO: Transit to following figure
-```{r fig.width=10, fig.height=5.5}
-ggplot(merged_data, aes(x = long, y = lat, group=group)) +
+```{r}
+figure3a <- read.csv(here::here("outputs/data/figure_3a.csv"))
+
+ggplot(figure3a, aes(x = long, y = lat, group=group)) +
   geom_polygon(aes(fill = brate1544_thsnds_ch_pct)) +

### 2024-02-13 scripts/02-data_cleaning.R

@@ -1,98 +1,86 @@
 #### Preamble ####
 # Purpose: Cleans the raw plane data
-# Author: Yuanyi (Leo) Liu
-# Date: 21 January 2024
-# Contact: leoy.liu@mail.utoronto.ca
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Date: 13 February 2024
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
 # License: MIT
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(dplyr)
+library(here)
+library(mapdata)
 
 
 #### Cleaned data ####
-raw_data <- read_csv("inputs/data/toronto_crime_rates.csv")
 
-# Removing unwanted columns
-cleaned_data <- raw_data %>% select(-c(X_id, HOOD_ID, POPULATION_2023, geometry))
+##Figure 1##
+figure1 <- read.csv(here::here("inputs/data/fig_1.csv"))
 
-# Removing rows with NA values
-cleaned_data <- na.omit(cleaned_data)
+#Write to CSV
+write_csv(
+  x = figure1,
+  file = "outputs/data/figure_1.csv"
+)
 
-# Save data #
+##Figure 2##
+uncleaned_data <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
+
+cleaned_data <- uncleaned_data |>
+  select(brate_1519, brate_2024, brate_2529, brate_3034, brate_3539, brate_4044, year)
+
+cleaned_data <- cleaned_data |>
+  rename(
+    "br_15 to 19" = brate_1519,
+    "br_20 to 24" = brate_2024,
+    "br_25 to 29" = brate_2529,
+    "br_30 to 34" = brate_3034,
+    "br_35 to 39" = brate_3539,
+    "br_40 to 44" = brate_4044,
+  )
+
+cleaned_data <- cleaned_data |>
+  pivot_longer(cols = starts_with("br_"),
+               names_to = "age_group",
+               names_prefix = "br_",
+               values_to = "brate")
+
+#Write to CSV
 write_csv(
   x = cleaned_data,
-  file = "cleaned_toronto_crime_rates.csv"
+  file = "outputs/data/figure_2.csv"
 )
 
-# Descriptive Summaries #
-str(cleaned_data)
-summary(cleaned_data)
+##Figure 3a##
 
[…]

### 2024-02-13 scripts/fig_1.R

@@ -1,13 +1,0 @@
-#Workspace set up
-
-library(tidyverse)
-library(dplyr)
-library(here)
-library(ggplot2)
-
-figure <- read.csv(here::here("inputs/data/fig_1.csv"))
-
-write_csv(
-  x = figure,
-  file = "outputs/data/figure_1.csv"
-)

### 2024-02-13 scripts/fig_2.R

@@ -1,30 +1,0 @@
-library(dplyr)
-library(tidyverse)
-library(here)
-library(ggplot2)
-
-uncleaned_data <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
-
-cleaned_data <- uncleaned_data |>
-  select(brate_1519, brate_2024, brate_2529, brate_3034, brate_3539, brate_4044, year)
-
-cleaned_data <- cleaned_data |>
-  rename(
-    "br_15 to 19" = brate_1519,
-    "br_20 to 24" = brate_2024,
-    "br_25 to 29" = brate_2529,
-    "br_30 to 34" = brate_3034,
-    "br_35 to 39" = brate_3539,
-    "br_40 to 44" = brate_4044,
-  )
-
-cleaned_data <- cleaned_data |>
-  pivot_longer(cols = starts_with("br_"),
-               names_to = "age_group",
-               names_prefix = "br_",
-               values_to = "brate")
-
-write_csv(
-  x = cleaned_data,
-  file = "outputs/data/figure_2.csv"
-)

### 2024-02-13 scripts/fig_3a.R

@@ -1,39 +1,0 @@
-library(tidyverse)
-library(dplyr)
-library(sf)
-library(here)
-library(ggplot2)
-library(mapdata)
-library(haven)
-
-uncleaned_data <- read.csv(here::here("inputs/data/fig_3.csv"))
-
-state <- map_data("state")
-
-#data <- read_dta(here::here('data/nchs/nchs_births_pop_1990_2019.dta'))
-
-cleaned_data <- uncleaned_data [-c(1, 12), ]
-
-state_full <- tibble(
-  stname=cleaned_data$stname,
-  full=c("alabama", "arkansas", "arizona", "california", "colorado", "connecticut", "district of columbia", "delaware",
-         "florida", "georgia", "iowa", "idaho", "illinois", "indiana", "kansas", "kentucky", "louisiana", "massachusetts", "maryland", "maine", "michigan",
-         "minnesota", "missouri", "mississippi", "montana", "north carolina", "north dakota", "nebraska", "new hampshire", "new jersey", "new mexico",
-         "nevada", "new york", "ohio", "oklahoma", "oregon", "pennsylvania", "rhode island", "south carolina", "south dakota",
-         "tennessee", "texas", "utah", "virginia", "vermont", "washington", "wisconsin","west virginia", "wyoming"
-         )
-)
-
-
-cleaned_data <- cleaned_data |>
-  left_join(state_full, by = "stname") |>
-  select(-stname) |>
-  rename(stname = full)
-
-
-merged_data <- merge(state, cleaned_data, by.x = "region", by.y = "stname", all.x = TRUE)
-
-write_csv(
-  x = merged_data,
-  file = "outputs/data/figure_3a.csv"
-)

### 2024-02-13 outputs/paper/paper.qmd
Update paper content, delete unnecessary file

@@
 #| message: false
+
+# install.packages("mapdata")
 
@@
 ## Source
+// TODO: Add explanation for source
 
-Although alternative datasets were considered, this specific dataset was selected for its detailed year-wise breakdown and the diversity of crime types it encompasses.
-Other datasets either lacked the temporal detail or the variety of crime categories present in our chosen dataset.
+Although alternative datasets were considered, this specific dataset was selected for its detailed year-wise breakdown and diversity.
+Other datasets either lacked the temporal detail or variety present in our chosen dataset.
 
 ## Methodology
-The data was processed and cleaned using R[@citeR], a powerful statistical programming language. For key operations, please refer to the [@sec-appendix].
+// TODO: Add methodology for cleaning data
+The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
 
 ## Variables
-To better understand the data, the summary_table dataset was developed to offer a more structured and aggregated view of the crime data.
-By transforming and summarizing the data into a format that displays crime types against years, this dataset simplifies the task of identifying and analyzing trends over time.
-The dataset includes various crime categories, such as assault, theft, and other types, with each variable representing the annual count of reported cases for each crime type.
-This longitudinal data provides a detailed view of the crime trends in Toronto over a decade.
+To better understand the data, the summary_table dataset was developed to offer a more structured and aggregated view of the birth rate data.
+By transforming and summarizing the data into a format that displays birth rate against years, this dataset simplifies the task of identifying and analyzing trends over time.
 
@@
 ```{r}
+#| label: fig-trends-in-birth-rate
+#| fig-cap: Trends in Birth Rate in US
+#| echo: false
 
@@
 ```
+@fig-trends-in-birth-rate, reflecting the trend in birth rates in America over time, captures a significant decline in birth rates commencing around the onset of the Great Recession in 2007-2008.
+According to Kearney et al.
+(2022), the economic stress associated with the Great Recession contributed to a marked downturn in birth rates, with a 7.2 percent drop from 68.1 to 63.2 births per 1,000 women observed between 2008 and 2011.
+This visual representation is particularly striking as it indicates a sharp and sustained decrease in birth rates coinciding with and following the Great Recession, without a subsequent recovery to pre-recession levels.
 
@@
 # Results {#sec-result}
-In this section, we delve into the core findings of our study, shedding light on the intricate patterns and trends of crime in Toronto from 2014 to 2023.
-Our analysis dissects both violent and non-violent crime statistics, revealing insightful correlations and variations over the decade.
+In this section, we delve into the core findings of our study, shedding light on the intricate patterns and trends of birth rate in US.
 
 ```{r}
+#| label: fig-trends-in-birth-rate-in-young-people
+#| fig-cap: Trends in Birth Rate Among Young People in US
+#| echo: false
+
 figure2 <- read.csv(here::here("outputs/data/figure_2.csv"))
@@
 ggplot(figure2, aes(x = year, y = brate, color = age_group)) +
-  geom_line(size=1) +
+  geom_line(linewidth=1) +
   geom_vline(xintercept = 2007, color = "black", linetype = "dashed") + 
@@
 ```
-// TODO: Explain the figure
+@fig-trends-in-birth-rate-in-young-people displays the birth rates segmented by age groups in the US from 1980 to 2020.
+Each line represents a different age bracket, showing distinct trends over time.
+The age groups range from 15-19 up to 40-44 years old.
+It is evident that the younger age groups experienced a decline in birth rates after 2007, the year marked as the beginning of the Great Recession.
+Notably, the youngest age group, 15-19, had a significant decrease from rates that were once the highest among the groups.
+In contrast, the 40-44 age group maintained the lowest birth rates throughout and saw a steafy slow increase.
 
@@
 ```{r}
+#| label: fig-demograph
+#| fig-cap: Demograph
+#| echo: false
+
 figure3a <- read.csv(here::here("outputs/data/figure_3a.csv"))
@@
 ```
-// TODO: Explain the figure
+@fig-demograph portrays the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
+The map's color gradient, which darkens with more significant decreases in birth rates, shows substantial variation across states.
+While the decline is widespread, some states, notably in the South, West, and in certain Southwestern and Mountain states, exhibit more significant decreases.
 
@@
 
-The analysis of Toronto's crime trends from 2014 to 2023 reveals a complex and evolving landscape of public safety.
-The pronounced increase in assault cases in recent years is alarming, suggesting that the city may be facing emerging challenges in maintaining public order.
-This rise in violent crime needs a closer investigation of possible causative factors, such as the effects of increased urbanization, economic disparity, and shifts in population density.
+// TODO
 
@@
 
-Simultaneously, the decline in theft-related crimes offers a more hopeful narrative.
-This trend may reflect the successful implementation of preventative measures by law enforcement agencies, such as community policing efforts and the integration of advanced surveillance technology.
-The use of crime prevention techniques, potentially aided by increased public awareness and education, appears to be bearing fruit.
+// TODO
 
@@
 
-The contrast between the trajectories of violent and non-violent crime rates underscores the need for a differentiated approach to policy-making and law enforcement.
-While we appreciate our gains in decreasing property crimes, the data motivates us to pursue more effective interventions for preventing and reacting to violent crimes.
-This might include extending social services, improving community engagement, and investing in data-driven police strategies.
+// TODO
 
@@
 
-While the visualization provides a high-level overview of crime trends in Toronto, it's essential to conduct a more detailed analysis to understand the underlying causes of these trends.
-This includes examining subcategories of crimes, focusing on specific geographic areas within the city, and considering other relevant data sources.
+// TODO
 
@@
 
-Furthermore, this study emphasises the need for ongoing monitoring and analysis of crime data to comprehend the ever-changing dynamics of urban crime.
-In light of these findings, future studies should focus on understanding the influence of specific policies and social changes on crime rates.
-Only by doing such a comprehensive analysis can we hope to develop strategies that will ensure the safety and well-being of all Toronto residents.
+// TODO
 
@@
 {{< pagebreak >}}
-
-# Appendix {#sec-appendix}
-## Data Manipulation and Cleaning
-* **Data Cleaning:** The initial phase of cleaning the Toronto crime rates dataset involved importing the raw data using the `read_csv` function from the `readr`[@citereadr] package.
-Following the import, the dataset was streamlined using the `select` function from `dplyr`[@citedplyr], a tidyverse[@citetidyverse] package, to remove irrelevant columns such as `X_id`, `HOOD_ID`, `POPULATION_2023`, and `geometry`.
-This step was crucial to focus the analysis on relevant variables.
-Additionally, the `na.omit` function was employed to discard any rows with missing values (NA), ensuring the dataset's completeness and reliability.
-The final step in the cleaning process was the exportation of the cleaned data into a new CSV file using the `write_csv `function from `readr`[@citereadr], thereby preserving the cleaned and refined dataset for subsequent analysis.
-
-* **Data Transformation:** The dataset was transformed from a wide format to a long format using the `gather` function from the `tidyr`[@citetidyr] package.
-This transformation is crucial for simplifying the data structure and making it more amenable to analysis.
-Also, the separate function, again from `tidyr`[@citetidyr], was instrumental in dividing the 'Crime_Year' column into two distinct parts: 'Crime_Type' and 'Year'.
-This enhances the granularity of the dataset, allowing for more detailed analysis.
-
-* **Aggregation:** The `group_by` and `summarise` functions from `dplyr`[@citedplyr] were employed to aggregate the data by year and crime type.
-
-* **Data Visualization:** For visual representation, `ggplot2`[@citeggplot], a versatile package in R for data visualization, was employed.
-It was used to create comprehensive line plots depicting the trends of various crime categories over the years.
-
-* **Paper Generation:** The packages `knitr`[@citeknitr] is used in generating R Markdown reports.

### 2024-02-13 outputs/paper/paper.qmd
methodology done

@@
 // TODO: Add methodology for cleaning data
+
 The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
+Moreover, most of the data in our dataset are previously cleaned in the project we are replicating.
+Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020.
+Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
+
+In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used R[@dpylr] to select the birth rate of the 6 age groups (from 15 to 44).
+Furthermore, the selected data was renamed using R[@tidyverse] and changed into names that represent the content of the data better.
+Moreover, these data is then pivoted using R[@tidyverse] in order to be graphed properly using R[@ggplot2].
+
+In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from R[@mapdata].
+The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from R[@mapdata].
+Then, a temporary data frame is created with tibble from R[@tidyverse] witht the the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from R[@dpylr], which is then selected and renamed using R[@tidyverse].
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing.
+
+In all three figures, the library R[@here] were used to ensure file path is accessible in all directories.
 

### 2024-02-13 outputs/paper/paper.qmd
Finished variable table, removed todo for metho d and vriable, added explaination for variable as well.

@@
 # install.packages("mapdata")
+# install.packages("kableExtra")
 
@@
 library(haven)
+library(kableExtra)
 ```
@@
 ## Methodology
-// TODO: Add methodology for cleaning data
-
 The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
@@
 Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from R[@dpylr], which is then selected and renamed using R[@tidyverse].
-After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing.
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with R[@heaven].
 
@@
 
-TODO: Add a table here to better understand the data.
 ```{r}
+#| label: tab-display-raw-data
+#| tbl-cap: Birth rate of all groups from 1980 to 1989
+#| echo: false
+
+rawdata <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
+
+rawdata |>
+  select(year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044,brate_whitenh,brate_blacknh,brate_hisp) |>
+  slice(1:10) |>
+  kable(
+    caption = "Birth rate of all groups from 1980 to 1989",
+    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "white", "black", "hispanic"),
+    digits = 1,
+    booktabs = TRUE
+  )
 ```
+
+This table presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
+Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
+The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years.
+Moreover, the last three columns are ethnic groups that describes the birth rates among the white, black, and Hispanic populations.
+However, some data for these groups are not available except 1989.
 

### 2024-02-13 outputs/paper/paper.qmd
Fix content

--- 2024-02-13 outputs/paper/paper.qmd
@@
 // TODO: Add methodology for cleaning data
+
 The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
+Moreover, most of the data in our dataset are previously cleaned in the project we are replicating.
+Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020.
+Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
+
+In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@dpylr] to select the birth rate of the 6 age groups (from 15 to 44).
+Furthermore, the selected data was renamed using `tidyverse`[@tidyverse] and changed into names that represent the content of the data better.
+Moreover, these data is then pivoted using `tidyverse`[@tidyverse] in order to be graphed properly using `ggplot2`[@ggplot2].
+
+In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from `mapdata`[@mapdata].
+The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from `mapdata`[@mapdata].
+Then, a temporary data frame is created with tibble from `tidyverse`[@tidyverse] with the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@dpylr], which is then selected and renamed using `tidyverse`[@tidyverse].
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing.
+
+In all three figures, the library `here`[@here] were used to ensure file path is accessible in all directories.
 

### 2024-02-13 outputs/paper/paper.qmd
fix content

@@
 Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@dpylr], which is then selected and renamed using `tidyverse`[@tidyverse].
-After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing.
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `heaven`[@heaven].
 

### 2024-02-13 outputs/paper/paper.qmd
Update reference and add content for introduction

--- 2024-02-13 outputs/paper/paper.qmd
@@
 
-This section aims to offer an insightful understanding of the dataset utilized in our analysis, focusing on its content, origin, and the methods applied for data manipulation and visualization.
+This section aims to offer an insightful understanding of the dataset utilized in our analysis.
+The dataset captures the birth rates across various demographics in the United States from 1980 to 2020.
+The data provide a broader context, allowing an analysis of trends over time and across different economic cycles, including the period of the Great Recession.
 
@@
 
-Although alternative datasets were considered, this specific dataset was selected for its detailed year-wise breakdown and diversity.
-Other datasets either lacked the temporal detail or variety present in our chosen dataset.
+While there were alternative datasets available from other public and private sources, this dataset was chosen due to its comprehensive coverage, reliability, and the level of detail it offers.
+It includes data from the National Center for Health Statistics (NCHS) and the U.S.
+Census Bureau, which are both reputable sources of demographic data.
 
@@
 
-In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used R[@dpylr] to select the birth rate of the 6 age groups (from 15 to 44).
-Furthermore, the selected data was renamed using R[@tidyverse] and changed into names that represent the content of the data better.
-Moreover, these data is then pivoted using R[@tidyverse] in order to be graphed properly using R[@ggplot2].
+In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rate of the 6 age groups (from 15 to 44).
+Furthermore, the selected data was renamed using `tidyverse`[@citetidyverse] and changed into names that represent the content of the data better.
+Moreover, these data is then pivoted using `tidyverse`[@citetidyverse] in order to be graphed properly using `ggplot2`[@citeggplot].
 
-In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from R[@mapdata].
-The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from R[@mapdata].
-Then, a temporary data frame is created with tibble from R[@tidyverse] witht the the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
-Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from R[@dpylr], which is then selected and renamed using R[@tidyverse].
-After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with R[@heaven].
+In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from `mapdata`.
+The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from `mapdata`.
+Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven`[@citehaven].
 
-In all three figures, the library R[@here] were used to ensure file path is accessible in all directories.
+// TODO: kable
+
+In all three figures, the library `here` were used to ensure file path is accessible in all directories.
 
@@
 ```{r}
-#| label: tab-display-raw-data
+#| label: tbl-display-raw-data
 #| tbl-cap: Birth rate of all groups from 1980 to 1989

### 2024-02-13 outputs/paper/paper.qmd
Add content for Result

@@
 // Visualization of the data for intuition
+
+## Measurements
+
+// TODO: Add a summary table to show measurements
+
+\newpage
+
+# Results {#sec-result}
+
+@sec-result presents the core findings from our comprehensive analysis of US birth rates, specifically focusing on the changes observed over time, across different age groups of young women, and by state.
+
+## Overall Trend in US Birth Rates
 ```{r}
@@
 ```
+First, we examine the overall trend, showcasing a substantial decline following the Great Recession.
 @fig-trends-in-birth-rate, reflecting the trend in birth rates in America over time, captures a significant decline in birth rates commencing around the onset of the Great Recession in 2007-2008.
@@
 
-## Measurements
-
-// TODO: Add a summary table to show measurements
-
-\newpage
-
-# Results {#sec-result}
-In this section, we delve into the core findings of our study, shedding light on the intricate patterns and trends of birth rate in US.
-
+## Trend in birth rate among yong women
 ```{r}
@@
 ```
+Transitioning to age-specific trends, we direct our attention to the young women's demographic.
 @fig-trends-in-birth-rate-in-young-people displays the birth rates segmented by age groups in the US from 1980 to 2020.
@@
 
-// TODO: Transit to following figure
+## Change in Birth Rates by State
 ```{r}
@@
 ```
-@fig-demograph portrays the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
+We then shift our focus to geographical variations in birth rates across states, presented in @fig-demograph.
+The graph portrays the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
 The map's color gradient, which darkens with more significant decreases in birth rates, shows substantial variation across states.
 While the decline is widespread, some states, notably in the South, West, and in certain Southwestern and Mountain states, exhibit more significant decreases.
+
+In summary, our results encapsulate a comprehensive view of the declining birth rates in the U.S., revealing both temporal and demographic patterns.
+The forthcoming @sec-discussion will delve into the potential influences and biases that may underlie these trends.
 

### 2024-02-14 outputs/paper/paper.qmd
resolve merge conflict

--- 2024-02-13 outputs/paper/paper.qmd
@@
 This research contributes to our understanding of how macroeconomic factors can have profound effects on personal life choices, emphasizing the need for supportive policies targeting young individuals during economic crises."
-format: pdf
+format: html
 toc: true
@@
         theme(panel.background = element_rect(fill = "white"),
-              plot.background = element_rect(fill = "white", color = NA),
+              panel.grid.major = element_line(colour = "grey"),
               plot.title = element_text(color = "black", size = 14, face = "bold"),
@@
   theme(panel.background = element_rect(fill = "white"),
-        plot.background = element_rect(fill = "white", color = NA),
+              panel.grid.major = element_line(colour = "grey"),
               plot.title = element_text(color = "black", size = 14, face = "bold"),

### 2024-02-14 outputs/paper/paper.qmd
Update paper content

--- 2024-02-13 outputs/paper/paper.qmd
@@
     caption = "Birth rate of all groups from 1980 to 1989",
-    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "white", "black", "hispanic"),
+    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "White", "Black", "Hispanic"),
     digits = 1,
@@
 
-This table presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
+@tbl-display-raw-data presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
 Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
@@
 However, some data for these groups are not available except 1989.
-
-// Visualization of the data for intuition
 
@@
 #| label: fig-trends-in-birth-rate
-#| fig-cap: Trends in Birth Rate in US
+#| fig-cap: Trend in Birth Rates in US
 #| echo: false
@@
 
-## Trend in birth rate among yong women
+## Trends in Birth Rates by Age Group
 ```{r}
 #| label: fig-trends-in-birth-rate-in-young-people
-#| fig-cap: Trends in Birth Rate Among Young People in US
+#| fig-cap: Trends in Birth Rates by Age Group
 #| echo: false
@@
 ```{r}
-#| label: fig-demograph
-#| fig-cap: Demograph
+#| label: fig-change-in-birth-rates-by-state
+#| fig-cap: Change in Birth Rates by State, 2004–2008 to 2015–2019
 #| echo: false
@@
 ```
-We then shift our focus to geographical variations in birth rates across states, presented in @fig-demograph.
+We then shift our focus to geographical variations in birth rates across states, presented in @fig-change-in-birth-rates-by-state.
 The graph portrays the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
@@
 
-// TODO
+The findings of this study offer a layered perspective on the decline in birth rates among young people in the United States, particularly in the context of the Great Recession.
+Our analysis provides a nuanced understanding of the multifaceted influences on demographic trends.
 
@@
 
-// TODO
+In our replication of Kearney et al.
+(2022), we reaffirmed the central finding that the Great Recession has had a lasting impact on birth rates among young people in the United States.
+Our analysis of Figures 1 and 2a showed a pronounced decline in birth rates across all age groups, with the steepest decrease observed among those aged 15-29.
+This trend extended beyond the economic recovery, suggesting that the Great Recession may have fundamentally altered the family planning trajectory of a generation.
 
@@
 
-// TODO
+The data presented in our study underscores the profound influence of economic factors on birth rates among young Americans, particularly in the wake of the Great Recession.
+The decline in birth rates aligns temporally with the economic downturn, suggesting a direct correlation between financial uncertainty and decisions regarding family planning.
+This is consistent with Kearney et al.
+(2022), who also observed a notable decrease in birth rates post-2007.
+Our findings further delve into the nuances of this relationship, illustrating how economic stressors extend beyond immediate financial strain to influence long-term life choices.
+The persistence of this trend, despite economic recovery, indicates a lasting impact on the psyche of young individuals, potentially altering their perception of financial stability and its importance in family planning.
+This insight points to the need for economic policies that provide not only immediate relief but also long-term security to mitigate such profound impacts on demographic trends.
 
@@
 
-// TODO
+Our analysis also highlights the role of societal and technological changes in shaping birth rate trends among young people.
+The significant decline in birth rates within the 15-29 age group, as detailed in our findings, suggests a shift in life priorities that may be influenced by broader societal changes.
+These include increased access to higher education, career opportunities, and advancements in reproductive technology, which have provided young people with more choices and greater control over their reproductive decisions.
+This is in line with the observations made by Kearney et al.
+(2022), who speculated on the influence of shifting priorities and the second demographic transition.
+Our study expands on this by suggesting that the integration of technology and societal evolution has created a new landscape for family planning, where traditional timelines and expectations may no longer hold the same weight.
+This evolution points to the necessity of incorporating societal and technological considerations into policy-making to address the changing dynamics of family planning in the modern era.
 
@@
 
-// TODO
+One limitation of our study is the potential for unobserved variables that could affect birth rates, such as cultural shifts and changes in social norms, which were not fully captured in the data.
+Additionally, the original study did not account for the influence of the Affordable Care Act and its potential impact on family planning decisions, an area our study also does not explore.
 
@@
 
-// TODO
+Future research should aim to disentangle these complex relationships further, perhaps through longitudinal studies or by incorporating more granular data on individual socioeconomic status.
+Understanding these dynamics is crucial for developing policies that support young people in their family planning decisions during and after economic downturns.
 

### 2024-02-14 outputs/paper/paper.qmd
fixed table, resolve merge conflict

@@
 
-// TODO: kable
-
 In all three figures, the library `here` were used to ensure file path is accessible in all directories.
@@
 
-@tbl-display-raw-data presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
+@tbl-display-raw-data uses R[@kable] presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
 Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
@@
 However, some data for these groups are not available except 1989.
+
+// Visualization of the data for intuition
 

### 2024-02-14 outputs/paper/paper.qmd
fixed table

@@
 This research contributes to our understanding of how macroeconomic factors can have profound effects on personal life choices, emphasizing the need for supportive policies targeting young individuals during economic crises."
-format: html
+format: pdf
 toc: true

### 2024-02-14 outputs/paper/paper.qmd
Add Measurement and estimand

@@
 
+In this study, our primary estimand is the causal effect of the Great Recession on the birth rates among young people in the United States.
+Specifically, we aim to estimate the magnitude of change in birth rates attributable to the economic downturn, distinguishing this effect from other contemporaneous social and economic factors.
+This involves analyzing the differential impact of the recession on various age groups and across states, providing a nuanced understanding of how macroeconomic shocks can influence demographic trends.
+
 The paper is structured to facilitate a comprehensive understanding of the study and its implications.
@@
 @sec-discussion provides an in-depth discussion of these findings, exploring potential factors influencing these trends, drawing connections to broader socio-economic issues, and providing suggestions for future research in this area.
-
-\newpage
 
@@
 ## Variables
+
 To better understand the data, the summary_table dataset was developed to offer a more structured and aggregated view of the birth rate data.
@@
 
-// Visualization of the data for intuition
-
 ## Measurements
 
-// TODO: Add a summary table to show measurements
+The measurement of birth rates in our study involves a detailed analysis of the annual number of live births per 1,000 women in various age groups, ranging from 15 to 44 years.
+These rates were extracted from comprehensive datasets provided by the National Center for Health Statistics (NCHS) and the U.S.
+Census Bureau, ensuring accuracy and reliability in capturing demographic trends across the United States from 1980 to 2020.
+
+For each age group, birth rates were calculated by dividing the total number of live births by the population of women in that age range, then multiplying by 1,000 to standardize the measure.
+This approach allows for comparison across different demographics and time periods, providing a clear picture of how birth rates have shifted, particularly in response to economic conditions such as the Great Recession.
+
+In addition to age-specific birth rates, state-level data were also analyzed to identify geographic variations in birth rate trends.
+This involved mapping birth rates against state populations, taking into consideration the exclusion of data from states like Alaska and Hawaii where mapping constraints exist.
 
@@
 
-The data presented in our study underscores the profound influence of economic factors on birth rates among young Americans, particularly in the wake of the Great Recession.
-The decline in birth rates aligns temporally with the economic downturn, suggesting a direct correlation between financial uncertainty and decisions regarding family planning.
-This is consistent with Kearney et al.
-(2022), who also observed a notable decrease in birth rates post-2007.
-Our findings further delve into the nuances of this relationship, illustrating how economic stressors extend beyond immediate financial strain to influence long-term life choices.
-The persistence of this trend, despite economic recovery, indicates a lasting impact on the psyche of young individuals, potentially altering their perception of financial stability and its importance in family planning.
-This insight points to the need for economic policies that provide not only immediate relief but also long-term security to mitigate such profound impacts on demographic trends.
+The significant decline in birth rates among young Americans during and after the Great Recession underscores the profound influence of economic stress on reproductive decisions.
+This downturn in birth rates is not merely coincidental with the timing of the recession but suggests a deeper, more systemic impact of economic instability on personal life choices, particularly the decision to start or expand a family.
+The persistence of this trend, even in the years following economic recovery, indicates that the repercussions of the recession extended beyond immediate financial hardship, affecting long-term perceptions of financial security and stability.
+This is further evidenced by the lack of rebound in birth rates post-recession, which might have been anticipated if the decline were solely due to immediate economic pressures.
+
+The economic model of fertility, which considers the cost of childbearing and rearing alongside the opportunity costs associated with parental time and resources, provides a framework to understand these trends.
+The recession likely heightened these costs and opportunity costs, making the decision to have children more daunting.
+Factors such as unemployment, underemployment, and job insecurity could have led to a reevaluation of the feasibility of affording children, contributing to the postponement or forego of childbirth.
+Additionally, the economic downturn might have altered young adults' expectations and aspirations regarding financial stability, further influencing their family planning decisions.
 
@@
 
-Our analysis also highlights the role of societal and technological changes in shaping birth rate trends among young people.
-The significant decline in birth rates within the 15-29 age group, as detailed in our findings, suggests a shift in life priorities that may be influenced by broader societal changes.
-These include increased access to higher education, career opportunities, and advancements in reproductive technology, which have provided young people with more choices and greater control over their reproductive decisions.
-This is in line with the observations made by Kearney et al.
-(2022), who speculated on the influence of shifting priorities and the second demographic transition.
-Our study expands on this by suggesting that the integration of technology and societal evolution has created a new landscape for family planning, where traditional timelines and expectations may no longer hold the same weight.
-This evolution points to the necessity of incorporating societal and technological considerations into policy-making to address the changing dynamics of family planning in the modern era.
+Apart from economic factors, the decline in birth rates among young people also reflects broader societal and technological shifts.
+The period following the Great Recession coincided with significant changes in social norms, increased educational and career opportunities for women, and advancements in reproductive technology.
+These factors collectively have empowered individuals, especially women, to make more autonomous decisions regarding their reproductive health and family planning.
+
+The rise in educational attainment and labor force participation among women has been accompanied by a corresponding increase in the opportunity cost of childbearing, potentially contributing to the decline in birth rates.
+Technological advancements, particularly in contraception, have provided women with greater control over their fertility, enabling more deliberate planning around childbirth.
+Social shifts, such as delayed marriage and the increasing acceptance of childlessness or smaller family sizes as viable lifestyle choices, further compound these trends.
+
+The interplay between these economic, societal, and technological factors has reshaped the landscape of family planning for young Americans.
+While the economic model of fertility provides a foundation for understanding these trends, the inclusion of societal and technological influences offers a more comprehensive picture of the forces at play in shaping contemporary birth rate patterns.
 

### 2024-02-14 outputs/paper/paper.qmd
fix spelling
replication done, variable finished delete race, added states

--- 2024-02-14 outputs/paper/paper.qmd
@@
 rawdata |>
-  select(year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044,brate_whitenh,brate_blacknh,brate_hisp) |>
+  select(year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044) |>
   slice(1:10) |>
@@
     caption = "Birth rate of all groups from 1980 to 1989",
-    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "White", "Black", "Hispanic"),
+    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44"),
     digits = 1,
@@
 The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years.
-Moreover, the last three columns are ethnic groups that describes the birth rates among the white, black, and Hispanic populations.
-However, some data for these groups are not available except 1989.
+Moreover, we are also concerned with the birth rate of related states in America.
 

### 2024-02-14 scripts/99-replications.R

@@ -1,0 +1,65 @@
+library(tidyverse)
+library(dplyr)
+library(here)
+library(mapdata)
+library(ggplot2)
+library(haven)
+
+#figure1
+figure1 <- read.csv(here::here("outputs/data/figure_1.csv"))
+
+ggplot(figure1,
+       aes(x = year, y = brate_all)) + 
+  geom_line(color="red") +
+  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") +
+  annotate("text", x = 2007, y = 60, label = "Global Financial Crisis of 2007-2008", 
+           color = "black", angle = 90, vjust = -0.5) +
+  labs(title = "Birth Rate in America overtime",
+       x = "Years",
+       y = "Birth rate") +
+  theme(panel.background = element_rect(fill = "white"),
+        panel.grid.major = element_line(colour = "grey"),
+        plot.title = element_text(color = "black", size = 14, face = "bold"),
+        axis.title = element_text(color = "black"))
+
+# Save plot
+ggsave(
+  "replication/graphs/figure1.png"
+)
+
+
+#figure2
+figure2 <- read.csv(here::here("outputs/data/figure_2.csv"))
+
+ggplot(figure2, aes(x = year, y = brate, color = age_group)) +
+  geom_line(linewidth=1) +
+  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") + 
+  annotate("text", x = 2007, y = 60, label = "2007", 
+           color = "black", angle = 90, vjust = -0.5) +
+  labs(title = "Birth Rate by Age Group Over Time",
+       x = "Year",
+       y = "Birth Rate") +
+  theme(panel.background = element_rect(fill = "white"),
+        panel.grid.major = element_line(colour = "grey"),
+        plot.title = element_text(color = "black", size = 14, face = "bold"),
+        axis.title = element_text(color = "black"))
+
+# Save plot
+ggsave(
+  "replication/graphs/figure2.png"
+)
+
+
+#Figure3
+figure3a <- read.csv(here::here("outputs/data/figure_3a.csv"))
+
+ggplot(figure3a, aes(x = long, y = lat, group=group)) +
+  geom_polygon(aes(fill = brate1544_thsnds_ch_pct)) +
+  scale_fill_gradient(low = 'darkred', high = '#FFCCCB') +
+  labs(title = 'Change in Birth Rate by State Over Time',
+       fill = 'Change in Birth Rate') +
[…]

### 2024-02-14 outputs/paper/paper.qmd

--- 2024-02-14 outputs/paper/paper.qmd
@@
 Following @sec-intro, @sec-data presents the data, detailing the data sources, analytical techniques, and the rationale behind the chosen methods.
-@sec-result discusses the results, elaborating on the observed trends and patterns in brth rate data.
+@sec-result discusses the results, elaborating on the observed trends and patterns in birth rate data.
 @sec-discussion provides an in-depth discussion of these findings, exploring potential factors influencing these trends, drawing connections to broader socio-economic issues, and providing suggestions for future research in this area.

### 2024-02-14 outputs/paper/paper.qmd
variable done, simulated data done, result done,

@@
 
-@tbl-display-raw-data uses R[@kable] presents the birth rates for various age groups and racial categories in the United States from the year 1980 to 1989.
-Moreover, the birth rates are typically expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
+@tbl-display-raw-data uses R[@citekableExtra] presents the birth rates for various age groups in the United States from the year 1980 to 1989.
+Moreover, the birth rates are expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
 The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years.
 Moreover, we are also concerned with the birth rate of related states in America.
+
+```{r}
+#| label: tbl-young-old-br
+#| tbl-cap: Birth rate of young and old age group from 1980 to 1989
+#| echo: false
+
+cleaned_data <- read.csv(here::here("outputs/data/table_2.csv"))
+
+cleaned_data |>
+  select(year, young, old) |>
+  slice(1:10) |>
+  kable(
+    caption = "Birth rate of young and old age group from 1980 to 1989",
+    col.names = c("Year", "Young", "Old"),
+    digits = 1,
+    booktabs = TRUE
+  )
+```
+
+@tbl-display-raw-data uses R[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
+This is a more concise table that represents the estimand we are trying to explore.
+Similarily to @tbl-display-raw-data, the birth rates are expressed by the mean birth rate of the selected age population.
+Moreover, the Year represent the years from the selected year range.
 
@@
 Notably, the youngest age group, 15-19, had a significant decrease from rates that were once the highest among the groups.
-In contrast, the 40-44 age group maintained the lowest birth rates throughout and saw a steafy slow increase.
+In contrast, the 40-44 age group maintained the lowest birth rates throughout and saw a steady slow increase.
+
+## Birth Rate Comparison between Young and Old Population
+```{r}
+#| label: fig-birth-rate-comparison-old-and-young
+#| fig-cap: Birth Rate Comparison between Young and Old Population
+#| echo: false
+
+figure4 <- read.csv(here::here("outputs/data/figure_4.csv"))
+
+ggplot(figure4, aes(x = year, y = brate, color = age_group)) +
+  geom_line(linewidth=1) +
+  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") + 
+  annotate("text", x = 2007, y = 60, label = "2007", 
+           color = "black", angle = 90, vjust = -0.5) +
+  labs(title = "Birth Rate Comparison between Young and Old Population",
+       x = "Year",
+       y = "Birth Rate") +
+  theme(panel.background = element_rect(fill = "white"),
+        panel.grid.major = element_line(colour = "grey"),
+        plot.title = element_text(color = "black", size = 14, face = "bold"),
+        axis.title = element_text(color = "black"))
+```
+To further visualize this birth rate change between age groups, we will categorize population between age 15 to 29 as young and the population between age 30 to 44 as old.
+The average birth rate of each group is calculated and displayed according to the corresponding year.
+The younger age group is represented by blue line and the older age group is represented by red line.
+It is evident from the graph that the younger age group is higher than that for the old population across the entire time span.
+However, it is also evident that there is a significant birth rate decrease in the young population after 2007, while older population maintains a slowly increasing trend.
+Moreover, it can be seen that the difference in birth rate between the two age groups is slowly decreasing, and from the current trend, this change in birth rate seems to be continuously dropping.
 

### 2024-02-14 scripts/00-simulate_data.R

@@ -1,38 +1,30 @@
 #### Preamble ####
 # Purpose: Simulates data
-# Author: Yuanyi (Leo) Liu
-# Email: leoy.liu@mail.utoronto.ca
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Email: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
 # Date: 21 January 2024
 # License: MIT
 
 
 #### Workspace setup ####
-# install.packages("janitor")
 # install.packages("tidyverse")
-library(janitor)
 library(tidyverse)
-
+library(dplyr)
 
 #### Simulate ####
 
-# In this simulation, we only want the number of cases reported of each crime type from 2014 to 2023.
-# First, A tibble is created with initial Crime_Type column.
-# Second, A loop runs through each year from 2014 to 2023.
-# In each iteration of the loop, a new column is added to simulated_data for the respective year. 
-# The sample function generates random counts for the crimes for that year.
-# Third, replace = TRUE in the sample function allows for the possibility of the same number being chosen more than once.
+# In this simulation, we only want two sets of birth rate data for two different age groups, young and old.
+# The simulated data is derived from a normal distribution instead of a poisson distribution since birth rate can be more than just integers.
+# It is ensured with the abs() that old positive birth rate is recorded.
 
 set.seed(853)
 
-crime_types <- c("Assault", "Auto Theft", "Bike Theft", "Break and Enter", "Homicide", "Robbery", "Shooting Incidents", "Theft from Motor Vehicles", "Major Theft")
-
 # Initialize a tibble
-simulated_data <- tibble(Crime_Type = crime_types)
-
-# Add columns for each year from 2014 to 2023 with simulated data
-for(year in 2014:2023) {
-  simulated_data[[as.character(year)]] <- sample(500:10000, length(crime_types), replace = TRUE)
-}
+simulated_data <- tibble(
+  year = c(1980:2020),
+    old = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
+  young = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
+)
 
 # View the simulated data
 print(simulated_data)

### 2024-02-14 scripts/02-data_cleaning.R

@@ -84,3 +84,40 @@ write_csv(
   x = merged_data,
   file = "outputs/data/figure_3a.csv"
 )
+
+##Figure 4##
+rawdata <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
+
+figure4 <- rawdata |>
+  select(
+    year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044
+  )
+
+figure4$young <- figure4 |>
+  select(
+    brate_1519,brate_2024,brate_2529
+  ) |>
+  rowMeans()
+
+figure4$old <- figure4 |>
+  select(
+    brate_3034,brate_3539,brate_4044
+  ) |>
+  rowMeans()
+
+#Write to CSV
+write_csv(
+  x = figure4,
+  file = "outputs/data/table_2.csv"
+)
+
+figure4 <- figure4 |>
+  pivot_longer(cols = c("young", "old"),
+               names_to = "age_group",
+               values_to = "brate")
+
+#Write to CSV
+write_csv(
+  x = figure4,
+  file = "outputs/data/figure_4.csv"
+)

### 2024-02-14 scripts/03-test_data.R

@@ -1,8 +1,8 @@
 #### Preamble ####
 # Purpose: Tests
-# Author: Yuanyi (Leo) Liu
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
 # Date: 24 January 2024
-# Contact: leoy.liu@mail.utoronto.ca
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
 # License: MIT
 
 

### 2024-02-14 scripts/99-replications.R

@@ -1,3 +1,10 @@
+#### Preamble ####
+# Purpose: Replicates graphs from targeted project
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Date: 14 February 2024
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
+# License: MIT
+
 library(tidyverse)
 library(dplyr)
 library(here)

### 2024-02-14 outputs/paper/paper.qmd
fix some errors

--- 2024-02-14 outputs/paper/paper.qmd
@@
 Our methodology involved analyzing birth rate data in conjunction with economic indicators such as unemployment rates, income levels, and housing market trends to draw correlations and insights.
+// TODO
 
@@
 While there were alternative datasets available from other public and private sources, this dataset was chosen due to its comprehensive coverage, reliability, and the level of detail it offers.
-It includes data from the National Center for Health Statistics (NCHS) and the U.S.
-Census Bureau, which are both reputable sources of demographic data.
+It includes data from the National Center for Health Statistics (NCHS) [TODO] and the U.S.
+Census Bureau [TODO], which are both reputable sources of demographic data.
 
 ## Methodology
+// TODO
+
 The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
@@
 rawdata |>
-  select(year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044) |>
+  select(year,brate_1519,brate_2024,brate_2529,brate_3034,brate_3539,brate_4044,brate_whitenh,brate_blacknh,brate_hisp) |>
   slice(1:10) |>
@@
     caption = "Birth rate of all groups from 1980 to 1989",
-    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44"),
+    col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44", "White", "Black", "Hispanic"),
     digits = 1,
@@
 The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years.
-Moreover, we are also concerned with the birth rate of related states in America.
+Moreover, the last three columns are ethnic groups that describes the birth rates among the white, black, and Hispanic populations.
+However, some data for these groups are not available except 1989.
 

### 2024-02-15 scripts/00-simulate_data.R
fixed group

@@ -22,8 +22,8 @@ set.seed(853)
 # Initialize a tibble
 simulated_data <- tibble(
   year = c(1980:2020),
-    old = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
-  young = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
+    young = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
+  old = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
 )
 
 # View the simulated data

### 2024-02-15 outputs/paper/paper.qmd
fixed wrong table reference
fixed simulation, and figure caption

--- 2024-02-14 outputs/paper/paper.qmd
@@
 #| label: tbl-young-old-br
-#| tbl-cap: Birth rate of young and old age group from 1980 to 1989
+#| tbl-cap: Birth rate of young and old from 1980 to 1989
 #| echo: false
@@
 
-@tbl-display-raw-data uses R[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
+@tbl-young-old-br uses R[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
 This is a more concise table that represents the estimand we are trying to explore.
@@
 #| label: fig-birth-rate-comparison-old-and-young
-#| fig-cap: Birth Rate Comparison between Young and Old Population
+#| fig-cap: Birth Rate between Young and Old Population
 #| echo: false
@@
            color = "black", angle = 90, vjust = -0.5) +
-  labs(title = "Birth Rate Comparison between Young and Old Population",
+  labs(title = "Birth Rate between Young and Old Population",
        x = "Year",

### 2024-02-15 scripts/00-simulate_data.R

@@ -14,7 +14,8 @@ library(dplyr)
 #### Simulate ####
 
 # In this simulation, we only want two sets of birth rate data for two different age groups, young and old.
-# The simulated data is derived from a normal distribution instead of a poisson distribution since birth rate can be more than just integers.
+# The simulation start with birth rate of 6 age groups.
+# The data is derived from a normal distribution instead of a poisson distribution since birth rate can be more than just integers.
 # It is ensured with the abs() that old positive birth rate is recorded.
 
 set.seed(853)
@@ -22,9 +23,25 @@ set.seed(853)
 # Initialize a tibble
 simulated_data <- tibble(
   year = c(1980:2020),
-    young = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
-  old = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
+  br_1519 = abs(rnorm(n = 41,mean = 50.5, sd=10.5)),
+  br_2024 = abs(rnorm(n = 41,mean = 55.5, sd=10.5)),
+  br_2529 = abs(rnorm(n = 41,mean = 80.5, sd=5.5)),
+  br_3034 = abs(rnorm(n = 41,mean = 55.5, sd=5.5)),
+  br_3539 = abs(rnorm(n = 41,mean = 35.5, sd=5.5)),
+  br_4044 = abs(rnorm(n = 41,mean = 25.5, sd=5.5)),
 )
+
+simulated_data$young <- simulated_data |>
+  select(
+    br_1519,br_2024,br_2529
+  ) |>
+  rowMeans()
+
+simulated_data$old <- simulated_data |>
+  select(
+    br_3034,br_3539,br_4044
+  ) |>
+  rowMeans()
 
 # View the simulated data
 print(simulated_data)

### 2024-02-15 outputs/paper/paper.qmd
update content

--- 2024-02-14 outputs/paper/paper.qmd
@@
   - Qi Er (Emma) Teng
-thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-s-Impact-on-Young-Americans-Birth-Rates/tree/main.
+thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-Impact-on-Young-Americans-Birth-Rates.
 A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802"
@@
 
+# install.packages("tidyverse")
+# install.packages("dplyr")
+# install.packages("here")
 # install.packages("mapdata")
+# install.packages("ggplot2")
+# install.packages("haven")
 # install.packages("kableExtra")
@@
 
-To better understand the data, the summary_table dataset was developed to offer a more structured and aggregated view of the birth rate data.
-By transforming and summarizing the data into a format that displays birth rate against years, this dataset simplifies the task of identifying and analyzing trends over time.
+To better understand the data, a summary table was developed to provide a detailed description of each variable, explaining its relevance and how it contributes to our understanding of the topic.
+Our focus is not only on the direct measures of birth rates but also on a range of demographic and economic variables that offer a comprehensive view of the factors influencing fertility decisions during the recessionary period.
 
@@
 ```
-
-@tbl-display-raw-data uses R[@citekableExtra] presents the birth rates for various age groups in the United States from the year 1980 to 1989.
+@tbl-display-raw-data uses `kableExtra`[@citekableExtra] presents the birth rates for various age groups in the United States from the year 1980 to 1989.
 Moreover, the birth rates are expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
@@
 ```
-
-@tbl-display-raw-data uses R[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
+@tbl-young-old-br uses `kableExtra`[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
 This is a more concise table that represents the estimand we are trying to explore.

### 2024-02-15 scripts/00-simulate_data.R

@@ -2,28 +2,32 @@
 # Purpose: Simulates data
 # Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
 # Email: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
-# Date: 21 January 2024
+# Date: 8 February 2024
 # License: MIT
 
 
 #### Workspace setup ####
 # install.packages("tidyverse")
+# install.packages("dplyr")
+
 library(tidyverse)
 library(dplyr)
 
+
 #### Simulate ####
 
-# In this simulation, we only want two sets of birth rate data for two different age groups, young and old.
+# In this simulation, we focus on two different age categories for birth rate data: younger and older groups.
 # The simulated data is derived from a normal distribution instead of a poisson distribution since birth rate can be more than just integers.
-# It is ensured with the abs() that old positive birth rate is recorded.
+# By applying the abs() function, we guarantee the recording of only positive birth rates for the older age group.
 
 set.seed(853)
 
 # Initialize a tibble
+# TODO:是不是写反了
 simulated_data <- tibble(
   year = c(1980:2020),
-    old = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
-  young = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
+    Elder = abs(rnorm(n = 41,mean = 80.5, sd=10.5)),
+  Younger = abs(rnorm(n = 41,mean = 25.5, sd=5.5))
 )
 
 # View the simulated data

### 2024-02-15 scripts/02-data_cleaning.R

@@ -15,16 +15,18 @@ library(mapdata)
 
 #### Cleaned data ####
 
-##Figure 1##
+
+## Figure 1 ##
 figure1 <- read.csv(here::here("inputs/data/fig_1.csv"))
 
-#Write to CSV
+# Write to CSV
 write_csv(
   x = figure1,
   file = "outputs/data/figure_1.csv"
 )
 
-##Figure 2##
+
+## Figure 2 ##
 uncleaned_data <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
 
 cleaned_data <- uncleaned_data |>
@@ -46,18 +48,19 @@ cleaned_data <- cleaned_data |>
                names_prefix = "br_",
                values_to = "brate")
 
-#Write to CSV
+# Write to CSV
 write_csv(
   x = cleaned_data,
   file = "outputs/data/figure_2.csv"
 )
 
-##Figure 3a##
 
+## Figure 3 ##
 uncleaned_data <- read.csv(here::here("inputs/data/fig_3.csv"))
 
 state <- map_data("state")
 
+## TODO?
 #data <- read_dta(here::here('data/nchs/nchs_births_pop_1990_2019.dta'))
 
 cleaned_data <- uncleaned_data [-c(1, 12), ]
@@ -79,13 +82,14 @@ cleaned_data <- cleaned_data |>
 
 merged_data <- merge(state, cleaned_data, by.x = "region", by.y = "stname", all.x = TRUE)
 
-#Write to CSV
+# Write to CSV
 write_csv(
   x = merged_data,
   file = "outputs/data/figure_3a.csv"
 )
 
-##Figure 4##
+
+## Figure 4 ##
 rawdata <- read.csv(here::here("inputs/data/figs_2a_2b.csv"))
 
 figure4 <- rawdata |>
@@ -105,7 +109,7 @@ figure4$old <- figure4 |>
   ) |>
   rowMeans()
 
-#Write to CSV
+# Write to CSV
 write_csv(
   x = figure4,
   file = "outputs/data/table_2.csv"
@@ -116,7 +120,7 @@ figure4 <- figure4 |>
                names_to = "age_group",
                values_to = "brate")
 
-#Write to CSV
+# Write to CSV
 write_csv(
   x = figure4,
   file = "outputs/data/figure_4.csv"

### 2024-02-15 scripts/03-test_data.R

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Tests
 # Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
-# Date: 24 January 2024
+# Date: 13 February 2024
 # Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
 # License: MIT
 

### 2024-02-15 scripts/99-replications.R

@@ -5,6 +5,8 @@
 # Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
 # License: MIT
 
+
+#### Workspace setup ####
 library(tidyverse)
 library(dplyr)
 library(here)
@@ -12,7 +14,10 @@ library(mapdata)
 library(ggplot2)
 library(haven)
 
-#figure1
+
+#### Replications ####
+
+## Figure 1 ##
 figure1 <- read.csv(here::here("outputs/data/figure_1.csv"))
 
 ggplot(figure1,
@@ -35,7 +40,7 @@ ggsave(
 )
 
 
-#figure2
+## Figure 2 ##
 figure2 <- read.csv(here::here("outputs/data/figure_2.csv"))
 
 ggplot(figure2, aes(x = year, y = brate, color = age_group)) +
@@ -57,7 +62,7 @@ ggsave(
 )
 
 
-#Figure3
+## Figure 3 ##
 figure3a <- read.csv(here::here("outputs/data/figure_3a.csv"))
 
 ggplot(figure3a, aes(x = long, y = lat, group=group)) +

### 2024-02-15 outputs/paper/paper.qmd
Update Repo Structure

@@
 thanks: "Code and data are available at: https://github.com/leoyliu/Analyzing-the-Great-Recession-Impact-on-Young-Americans-Birth-Rates.
-A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-srs6-t802"
+A replication of various aspects in this paper are available at: https://doi.org/10.48152/ssrp-ddvc-b340."
 date: today
@@
 Utilizing a blend of quantitative data analysis and demographic research, we investigated birth rate trends among young adults during and following the recessionary period.
-Our methodology involved analyzing birth rate data in conjunction with economic indicators such as unemployment rates, income levels, and housing market trends to draw correlations and insights.
-// TODO
-
 Our findings reveal a significant decline in birth rates among young Americans during the recession, with lingering effects in the subsequent years.
@@
 
-In this study, our primary estimand is the causal effect of the Great Recession on the birth rates among young people in the United States.
-Specifically, we aim to estimate the magnitude of change in birth rates attributable to the economic downturn, distinguishing this effect from other contemporaneous social and economic factors.
-This involves analyzing the differential impact of the recession on various age groups and across states, providing a nuanced understanding of how macroeconomic shocks can influence demographic trends.
+In this study, our primary estimand is the causal effect of the Great Recession on birth rates among young Americans, quantified by the change in birth rates attributable to the economic downturn, isolated from other socio-economic factors.
+This involves analyzing the differential impact of the recession on various age groups and across states, providing an understanding of how macroeconomic shocks can influence demographic trends.
 
@@
 
-## Source
-// TODO: Add explanation for source
+## Source and Methodology
+Data on birth rates for women aged 15-44 were sourced from National Vital Statistics Reports covering 2015, 2019, and 2020 [@cite2015birth; @cite2019birth; @cite2020birth], compiled from birth certificates across the US and the District of Columbia.
+@citeoriginal provided aggregated birth data for six cohorts over five-year spans, derived from NBER Natality Database [@citeNBER] and NCHS microdata [@citeNCHS] for 1980-2019.
+In this study, we simply used the replication data package provided by @citeoriginal for analysis.
 
 While there were alternative datasets available from other public and private sources, this dataset was chosen due to its comprehensive coverage, reliability, and the level of detail it offers.
-It includes data from the National Center for Health Statistics (NCHS) [TODO] and the U.S.
-Census Bureau [TODO], which are both reputable sources of demographic data.
+It includes data from the National Center for Health Statistics (NCHS) [@citeNCHS] and the U.S.
+Census Bureau [@citeUSCB], which are both reputable sources of demographic data.
 
-## Methodology
-// TODO
-
-The data was processed and cleaned using R[@citeR], a powerful statistical programming language.
-Moreover, most of the data in our dataset are previously cleaned in the project we are replicating.
-Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020.
-Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
-
-In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rate of the 6 age groups (from 15 to 44).
-Furthermore, the selected data was renamed using `tidyverse`[@citetidyverse] and changed into names that represent the content of the data better.
-Moreover, these data is then pivoted using `tidyverse`[@citetidyverse] in order to be graphed properly using `ggplot2`[@citeggplot].
-
-In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from `mapdata`.
-The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from `mapdata`.
-Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
-Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
-After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven`[@citehaven].
-
-In all three figures, the library `here` were used to ensure file path is accessible in all directories.
+The data was processed and cleaned using R[@citeR], a powerful statistical programming language. For key operations, please refer to the [@sec-appendix].
 
@@
 #| label: tbl-display-raw-data
-#| tbl-cap: Birth rate of all groups from 1980 to 1989
+#| tbl-cap: First Ten Rows of Birth Rates Spanning from 1980 to 2020
 #| echo: false
@@
   kable(
-    caption = "Birth rate of all groups from 1980 to 1989",
     col.names = c("Year", "15 to 19", "20 to 24","25 to 29", "30 to 34", "35 to 39", "40 to 44"),
@@
 ```
-@tbl-display-raw-data uses `kableExtra`[@citekableExtra] presents the birth rates for various age groups in the United States from the year 1980 to 1989.
-Moreover, the birth rates are expressed per every 1,000 women in the population.To further understand this table, Year represent the years from the selected year range.
-The next six columns are different age groups for women, which are 15 to 19 years, 20 to 24 years, 25 to 29 years, 30 to 34 years, 35 to 39 years, and 40 to 44 years.
-Moreover, we are also concerned with the birth rate of related states in America.
+@tbl-display-raw-data, created with `kableExtra` [@citekableExtra], showcases the first ten rows of U.S.
+birth rates by age group from 1980 to 2020, with rates per 1,000 women.
+To further understand this table, `Year` represents the specific years within this span.
+Following are six columns representing various age groups: 15-19, 20-24, 25-29, 30-34, 35-39, and 40-44 years.
+To examine the differences in birth rates between younger and older women, the data was aggregated into two age categories: `Younger` representing women aged 15-29, and `Older` for those aged 30-44.
+This aggregation facilitates a focused comparison across these distinct age groups.
 
@@
 #| label: tbl-young-old-br
-#| tbl-cap: Birth rate of young and old from 1980 to 1989
+#| tbl-cap: First Ten Rows of Birth Rates For Younger and Older Groups Spanning from 1980 to 2020
 #| echo: false
@@
   kable(
-    caption = "Birth rate of young and old age group from 1980 to 1989",
-    col.names = c("Year", "Young", "Old"),
+    col.names = c("Year", "Younger", "Older"),
     digits = 1,
@@
 ```
-@tbl-young-old-br uses `kableExtra`[@citekableExtra] presents the birth rates for the older and younger population from the year 1980 to 1989.
+@tbl-young-old-br, built with `kableExtra`[@citekableExtra], displays the first ten rows of birth rates for younger and older demographics from 1980 to 2020.
 This is a more concise table that represents the estimand we are trying to explore.
-Similarily to @tbl-display-raw-data, the birth rates are expressed by the mean birth rate of the selected age population.
-Moreover, the Year represent the years from the selected year range.
+Similar to @tbl-display-raw-data, it averages birth rates within selected age groups per year, providing a streamlined view for analysis.
 
@@
 The measurement of birth rates in our study involves a detailed analysis of the annual number of live births per 1,000 women in various age groups, ranging from 15 to 44 years.
-These rates were extracted from comprehensive datasets provided by the National Center for Health Statistics (NCHS) and the U.S.
-Census Bureau, ensuring accuracy and reliability in capturing demographic trends across the United States from 1980 to 2020.
+These rates were extracted from datasets provided by the National Center for Health Statistics (NCHS) [@citeNCHS], ensuring accuracy and reliability in capturing demographic trends across the United States from 1980 to 2020.
 
@@
 This involved mapping birth rates against state populations, taking into consideration the exclusion of data from states like Alaska and Hawaii where mapping constraints exist.
+Further details on this aspect of our study are discussed in @sec-result.
 
@@
 
-@sec-result presents the core findings from our comprehensive analysis of US birth rates, specifically focusing on the changes observed over time, across different age groups of young women, and by state.
+@sec-result presents the core findings from our analysis of US birth rates, specifically focusing on the changes observed over time, across different age groups of young women, and by state.
 
@@
 @fig-trends-in-birth-rate, reflecting the trend in birth rates in America over time, captures a significant decline in birth rates commencing around the onset of the Great Recession in 2007-2008.
-According to Kearney et al.
-(2022), the economic stress associated with the Great Recession contributed to a marked downturn in birth rates, with a 7.2 percent drop from 68.1 to 63.2 births per 1,000 women observed between 2008 and 2011.
+According to @citeoriginal, the economic stress associated with the Great Recession contributed to a marked downturn in birth rates, with a 7.2 percent drop from 68.1 to 63.2 births per 1,000 women observed between 2008 and 2011.
 This visual representation is particularly striking as it indicates a sharp and sustained decrease in birth rates coinciding with and following the Great Recession, without a subsequent recovery to pre-recession levels.
@@
 @fig-trends-in-birth-rate-in-young-people displays the birth rates segmented by age groups in the US from 1980 to 2020.
-Each line represents a different age bracket, showing distinct trends over time.
-The age groups range from 15-19 up to 40-44 years old.
+Each line represents a different age group, showing distinct trends over time.
 It is evident that the younger age groups experienced a decline in birth rates after 2007, the year marked as the beginning of the Great Recession.
@@
 The younger age group is represented by blue line and the older age group is represented by red line.
-It is evident from the graph that the younger age group is higher than that for the old population across the entire time span.
+It is evident from the @fig-birth-rate-comparison-old-and-young that the younger age group is higher than that for the old population across the entire time span.
 However, it is also evident that there is a significant birth rate decrease in the young population after 2007, while older population maintains a slowly increasing trend.
@@
 
-figure3a <- read.csv(here::here("outputs/data/figure_3a.csv"))
+figure3a <- read.csv(here::here("outputs/data/figure_3.csv"))
 
@@
 The findings of this study offer a layered perspective on the decline in birth rates among young people in the United States, particularly in the context of the Great Recession.
-Our analysis provides a nuanced understanding of the multifaceted influences on demographic trends.
+Our analysis provides an understanding of the multifaceted influences on demographic trends.
 
@@
 
-In our replication of Kearney et al.
-(2022), we reaffirmed the central finding that the Great Recession has had a lasting impact on birth rates among young people in the United States.
-Our analysis of Figures 1 and 2a showed a pronounced decline in birth rates across all age groups, with the steepest decrease observed among those aged 15-29.
+In our replication of @citeoriginal, we reaffirmed the central finding that the Great Recession has had a lasting impact on birth rates among young people in the United States.
+Our analysis of Figures 1 and 2 showed a pronounced decline in birth rates across all age groups, with the steepest decrease observed among those aged 15-29.
 This trend extended beyond the economic recovery, suggesting that the Great Recession may have fundamentally altered the family planning trajectory of a generation.
@@
 {{< pagebreak >}}
+
+# Appendix {#sec-appendix}
+## Data Manipulation and Cleaning
+Most of the data in our dataset are previously cleaned in the project we are replicating.
+Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020.
+Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
+
+In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rate of the 6 age groups (from 15 to 44).
+Furthermore, the selected data was renamed using `tidyverse`[@citetidyverse] and changed into names that represent the content of the data better.
+Moreover, these data is then pivoted using `tidyverse`[@citetidyverse] in order to be graphed properly using `ggplot2`[@citeggplot].
+
+In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from `mapdata` [@citemapdata].
+The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from `mapdata` [@citemapdata].
+Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven`[@citehaven].
+
+In all three figures, the library `here` [@citehere] were used to ensure file path is accessible in all directories.

### 2024-02-15 replications/scripts/fig1_replication.R

@@ -1,0 +1,70 @@
+#### Preamble ####
+# Purpose: Replicates graphs from targeted project
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Date: 14 February 2024
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
+# License: MIT
+
+# Portions of the code used to create visualizations were adapted from methodologies shared in the 
+# original paper and previous example (GitHub link: https://github.com/KCtt457/us-birth-rates-decline).
+
+#### Workspace setup ####
+# install.packages("tidyverse")
+# install.packages("ggprism")
+# install.packages("ggthemes")
+
+library(tidyverse)
+library(ggprism)
+library(ggthemes)
+
+
+#### Replications ####
+
+
+## Figure 2 ##
+
+# Read in the raw data
+fig1_data <- read_csv("inputs/data/fig_1.csv")
+
+# Make plot
+fig1_data %>%
+  ggplot(aes(x = year,
+             y = brate_all)) +
+  geom_line(color = "#08519C") +
+  geom_vline(xintercept = 2007,
+             linetype = "dashed",
+             color = "darkgrey") +
+  scale_x_continuous(
+    guide = "prism_minor",
+    limits = c(1980, 2020),
+    breaks = seq(1980, 2020, by = 5),
+    minor_breaks = seq(1980, 2020, by = 1)
+  ) +
+  scale_y_continuous(limits = c(50, 80), breaks = seq(50, 80, by = 5)) +
+  theme_classic() +
+  theme(
+    panel.grid.major.y = element_line(),
+    axis.ticks.length.x = unit(7, "pt"),
+    prism.ticks.length.x = unit(4, "pt")
+  ) +
+  geom_text(
+    aes(x = 2007, y = 70),
+    nudge_x = 2,
+    nudge_y = 1,
+    label = "2007"
+  ) +
+  labs(
+    title = "Trend in US Birth Rates",
+    x = "",
+    y = "Births per 1,000 women age 15-44",
+    caption = "Source: Birth Rates collected from CDC Vital Statistics Births Reports for 2015, 2019 and 2020."
+  )
+
+# Save plot
+ggsave(
+  "replication/plots/figure1.png",
+  height = 100,
+  width = 133.33,
+  units = "mm",
+  dpi = 900
+)

### 2024-02-15 replications/scripts/fig2_replication.R

@@ -1,0 +1,87 @@
+#### Preamble ####
+# Purpose: Replicates graphs from targeted project
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Date: 14 February 2024
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
+# License: MIT
+
+# Portions of the code used to create visualizations were adapted from methodologies shared in the 
+# original paper and previous example (GitHub link: https://github.com/KCtt457/us-birth-rates-decline).
+
+#### Workspace setup ####
+# install.packages("tidyverse")
+# install.packages("ggprism")
+# install.packages("ggthemes")
+
+library(tidyverse)
+library(ggprism)
+library(ggthemes)
+
+
+#### Replications ####
+
+
+## Figure 1 ##
+
+# Read in the raw data
+fig_2_data <- read_csv("inputs/data/figs_2a_2b.csv")
+
+# Data wrangling
+fig_2a_data <- fig_2_data %>%
+  select(-c(brate_whitenh, brate_blacknh, brate_hisp)) %>%
+  pivot_longer(-c(year), names_to = "age_group", values_to = "brate")
+
+# Make plot
+fig_2a_data %>%
+  ggplot(aes(x = year,
+             y = brate,
+             color = age_group)) +
+  geom_line() +
+  geom_vline(xintercept = 2007,
+             linetype = "dashed",
+             color = "darkgrey") +
+  scale_x_continuous(
+    guide = "prism_minor",
+    limits = c(1980, 2020),
+    breaks = seq(1980, 2020, by = 5),
+    minor_breaks = seq(1980, 2020, by = 1)
+  ) +
+  scale_y_continuous(limits = c(0, 140), breaks = seq(0, 140, by = 20)) +
+  scale_color_tableau(palette = "Color Blind") +
+  theme_classic() +
+  theme(
+    panel.grid.major.y = element_line(),
+    axis.ticks.length.x = unit(7, "pt"),
+    prism.ticks.length.x = unit(4, "pt"),
+    legend.position = "none"
+  ) +
+  geom_text(
+    aes(x = 2007, y = 120),
+    nudge_x = 2,
+    nudge_y = 7,
+    label = "2007",
+    color = "#000000"
+  ) +
+  geom_text(aes(x = 1985, y = 125), label = "Age 25-29", color = "#000000") +
+  geom_text(aes(x = 1985, y = 100), label = "Age 20-24", color = "#000000") +
[…]

### 2024-02-15 replications/scripts/fig3_replication.R

@@ -1,0 +1,33 @@
+#### Preamble ####
+# Purpose: Replicates graphs from targeted project
+# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
+# Date: 14 February 2024
+# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
+# License: MIT
+
+
+#### Workspace setup ####
+# install.packages("ggprism")
+# install.packages("ggthemes")
+
+library(tidyverse)
+
+
+#### Replications ####
+
+
+## Figure 3 ##
+
+# Read in the raw data
+figure3 <- read.csv(here::here("outputs/data/figure_3a.csv"))
+
+ggplot(figure3, aes(x = long, y = lat, group=group)) +
+  geom_polygon(aes(fill = brate1544_thsnds_ch_pct)) +
+  scale_fill_gradient(low = 'darkred', high = '#FFCCCB') +
+  labs(title = 'Change in Birth Rate by State Over Time',
+       fill = 'Change in Birth Rate') +
+  theme_void()
+
+ggsave(
+  "replication/plots/figure3.png"
+)

### 2024-02-15 scripts/01-download_data.R

@@ -1,31 +1,0 @@
-#### Preamble ####
-# Purpose: Downloads, saves, and reads data from the OpenDataToronto portal
-# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
-# Date: 13 February 2024
-# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
-# License: MIT
-
-
-#### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-library(dplyr)
-
-
-#### Download data ####
-# Each package is associated with a unique id  found in the "For 
-# Developers" tab of the relevant page from Open Data Toronto
-# source: https://open.toronto.ca/dataset/neighbourhood-crime-rates/
-toronto_crime_rates <-
-  list_package_resources("neighbourhood-crime-rates") |>
-  filter(name == "neighbourhood-crime-rates - 4326.csv") |>
-  get_resource()
-
-
-#### Save data ####
-write_csv(
-  x = toronto_crime_rates,
-  file = "toronto_crime_rates.csv"
-)
-
-head(toronto_crime_rates)

### 2024-02-15 scripts/99-replications.R

@@ -1,77 +1,0 @@
-#### Preamble ####
-# Purpose: Replicates graphs from targeted project
-# Author: Yuanyi (Leo) Liu, Qi Er (Emma) Teng
-# Date: 14 February 2024
-# Contact: leoy.liu@mail.utoronto.ca, e.teng@mail.utoronto.ca
-# License: MIT
-
-
-#### Workspace setup ####
-library(tidyverse)
-library(dplyr)
-library(here)
-library(mapdata)
-library(ggplot2)
-library(haven)
-
-
-#### Replications ####
-
-## Figure 1 ##
-figure1 <- read.csv(here::here("outputs/data/figure_1.csv"))
-
-ggplot(figure1,
-       aes(x = year, y = brate_all)) + 
-  geom_line(color="red") +
-  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") +
-  annotate("text", x = 2007, y = 60, label = "Global Financial Crisis of 2007-2008", 
-           color = "black", angle = 90, vjust = -0.5) +
-  labs(title = "Birth Rate in America overtime",
-       x = "Years",
-       y = "Birth rate") +
-  theme(panel.background = element_rect(fill = "white"),
-        panel.grid.major = element_line(colour = "grey"),
-        plot.title = element_text(color = "black", size = 14, face = "bold"),
-        axis.title = element_text(color = "black"))
-
-# Save plot
-ggsave(
-  "replication/graphs/figure1.png"
-)
-
-
-## Figure 2 ##
-figure2 <- read.csv(here::here("outputs/data/figure_2.csv"))
-
-ggplot(figure2, aes(x = year, y = brate, color = age_group)) +
-  geom_line(linewidth=1) +
-  geom_vline(xintercept = 2007, color = "black", linetype = "dashed") + 
-  annotate("text", x = 2007, y = 60, label = "2007", 
-           color = "black", angle = 90, vjust = -0.5) +
-  labs(title = "Birth Rate by Age Group Over Time",
-       x = "Year",
-       y = "Birth Rate") +
-  theme(panel.background = element_rect(fill = "white"),
-        panel.grid.major = element_line(colour = "grey"),
-        plot.title = element_text(color = "black", size = 14, face = "bold"),
-        axis.title = element_text(color = "black"))
-
-# Save plot
-ggsave(
-  "replication/graphs/figure2.png"
-)
-
-
[…]

### 2024-02-15 scripts/01-data_cleaning.R
update data cleaning

@@ -60,9 +60,6 @@ uncleaned_data <- read.csv(here::here("inputs/data/fig_3.csv"))
 
 state <- map_data("state")
 
-## TODO?
-#data <- read_dta(here::here('data/nchs/nchs_births_pop_1990_2019.dta'))
-
 cleaned_data <- uncleaned_data [-c(1, 12), ]
 
 state_full <- tibble(
@@ -85,7 +82,7 @@ merged_data <- merge(state, cleaned_data, by.x = "region", by.y = "stname", all.
 # Write to CSV
 write_csv(
   x = merged_data,
-  file = "outputs/data/figure_3a.csv"
+  file = "outputs/data/figure_3.csv"
 )
 
 

### 2024-02-15 outputs/paper/paper.qmd
Finalize the paper

@@
 Data on birth rates for women aged 15-44 were sourced from National Vital Statistics Reports covering 2015, 2019, and 2020 [@cite2015birth; @cite2019birth; @cite2020birth], compiled from birth certificates across the US and the District of Columbia.
-@citeoriginal provided aggregated birth data for six cohorts over five-year spans, derived from NBER Natality Database [@citeNBER] and NCHS microdata [@citeNCHS] for 1980-2019.
+@citeoriginal provided aggregated birth data for six cohorts over five-year spans, derived from the NBER Natality Database [@citeNBER] and NCHS microdata [@citeNCHS] for 1980-2019.
 In this study, we simply used the replication data package provided by @citeoriginal for analysis.
@@
 While there were alternative datasets available from other public and private sources, this dataset was chosen due to its comprehensive coverage, reliability, and the level of detail it offers.
-It includes data from the National Center for Health Statistics (NCHS) [@citeNCHS] and the U.S.
-Census Bureau [@citeUSCB], which are both reputable sources of demographic data.
+It includes data from the National Center for Health Statistics [@citeNCHS] and the U.S.
+Census Bureau, which are both reputable sources of demographic data.
 
@@
 Further details on this aspect of our study are discussed in @sec-result.
-
-\newpage
 
@@
 
-In summary, our results encapsulate a comprehensive view of the declining birth rates in the U.S., revealing both temporal and demographic patterns.
-The forthcoming @sec-discussion will delve into the potential influences and biases that may underlie these trends.
+In conclusion, our findings provide a complete perspective of dropping birth rates in the United States, demonstrating both temporal and demographic tendencies.
+The upcoming @sec-discussion will look at the various variables and biases that may be driving these trends.
 
@@
 
-The significant decline in birth rates among young Americans during and after the Great Recession underscores the profound influence of economic stress on reproductive decisions.
-This downturn in birth rates is not merely coincidental with the timing of the recession but suggests a deeper, more systemic impact of economic instability on personal life choices, particularly the decision to start or expand a family.
-The persistence of this trend, even in the years following economic recovery, indicates that the repercussions of the recession extended beyond immediate financial hardship, affecting long-term perceptions of financial security and stability.
+The dramatic drop in birth rates among young Americans during and after the Great Recession demonstrates the profound impact of economic hardship on reproductive decisions.
+This decline in birth rates is not simply coincidental with the date of the recession, but rather indicates a deeper, more systemic influence of economic insecurity on personal life choices, notably the decision to establish or expand a family.
+The persistence of this pattern, even in the years after economic recovery, suggests that the effects of the recession went beyond immediate financial hardship, influencing long-term views of financial security and stability.
 This is further evidenced by the lack of rebound in birth rates post-recession, which might have been anticipated if the decline were solely due to immediate economic pressures.
 
-The economic model of fertility, which considers the cost of childbearing and rearing alongside the opportunity costs associated with parental time and resources, provides a framework to understand these trends.
-The recession likely heightened these costs and opportunity costs, making the decision to have children more daunting.
-Factors such as unemployment, underemployment, and job insecurity could have led to a reevaluation of the feasibility of affording children, contributing to the postponement or forego of childbirth.
-Additionally, the economic downturn might have altered young adults' expectations and aspirations regarding financial stability, further influencing their family planning decisions.
+The economic model of fertility provides a framework for understanding these patterns by taking into account the cost of pregnancy and raising as well as the opportunity costs associated with parental time and resources.
+The recession likely increased these expenditures and opportunity costs, making the decision to have children more difficult.
+Unemployment and job uncertainty may have caused a reevaluation of the feasibility of having children, resulting in the postponement or avoidance of childbirth.
+Furthermore, the economic downturn may have shifted young adults' expectations and desires for financial security, impacting their family planning decisions.
 
@@
 The period following the Great Recession coincided with significant changes in social norms, increased educational and career opportunities for women, and advancements in reproductive technology.
-These factors collectively have empowered individuals, especially women, to make more autonomous decisions regarding their reproductive health and family planning.
+These factors collectively have empowered individuals, especially women, to make more independent decisions regarding their reproductive health and family planning.
 
-The rise in educational attainment and labor force participation among women has been accompanied by a corresponding increase in the opportunity cost of childbearing, potentially contributing to the decline in birth rates.
-Technological advancements, particularly in contraception, have provided women with greater control over their fertility, enabling more deliberate planning around childbirth.
-Social shifts, such as delayed marriage and the increasing acceptance of childlessness or smaller family sizes as viable lifestyle choices, further compound these trends.
+As women's educational attainment and labor force involvement have increased, so has the opportunity cost of childbirth, potentially contributing to the drop in birth rates.
+Technological developments have given women greater control over their fertility, allowing for more intentional planning around childbirth.
+Social changes, such as delayed marriage and a growing acceptance of childlessness or smaller family sizes as realistic lifestyle options, further compound these tendencies.
 
-The interplay between these economic, societal, and technological factors has reshaped the landscape of family planning for young Americans.
-While the economic model of fertility provides a foundation for understanding these trends, the inclusion of societal and technological influences offers a more comprehensive picture of the forces at play in shaping contemporary birth rate patterns.
+The interaction of these economic, social, and technical elements has altered the landscape of family planning for young Americans.
+While the economic model of fertility provides a framework for understanding these developments, including sociological and technical effects provides a more complete view of the dynamics affecting current birth rate patterns.
 
@@
 
-Future research should aim to disentangle these complex relationships further, perhaps through longitudinal studies or by incorporating more granular data on individual socioeconomic status.
+Future research should aim to disentangle these complex relationships further, perhaps through longitudinal studies or by incorporating more detailed data on individual socioeconomic status.
 Understanding these dynamics is crucial for developing policies that support young people in their family planning decisions during and after economic downturns.
@@
 ## Data Manipulation and Cleaning
-Most of the data in our dataset are previously cleaned in the project we are replicating.
-Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary as it simply displays the birth rate from 1980 to 2020.
+Most of the data in our dataset was previously cleaned for the project we are replicating.
+Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary, as it simply displays the birth rate from 1980 to 2020.
 Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
 
-In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rate of the 6 age groups (from 15 to 44).
+In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rates of the six age groups (from 15 to 44).
 Furthermore, the selected data was renamed using `tidyverse`[@citetidyverse] and changed into names that represent the content of the data better.
@@
 
-In figure 3, the first dataset was imported from `inputs/data/fig_3a.csv` and the dataset containing American states information was from `mapdata` [@citemapdata].
-The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii as these two states can't be properly showned in the dataset from `mapdata` [@citemapdata].
-Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3a.csv` and the state full names.
-Moreover, the abbreviated state name in the first dataset is switched with the state full names using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
+In figure 3, the first dataset was imported from `inputs/data/fig_3.csv` and the dataset containing American states information was from `mapdata` [@citemapdata].
+The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii, as these two states can't be properly shown in the dataset from `mapdata` [@citemapdata].
+Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full name using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
 After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven`[@citehaven].
 
-In all three figures, the library `here` [@citehere] were used to ensure file path is accessible in all directories.
+In all three figures, the library `here` [@citehere] was used to ensure that the file path should be accessible in all directories.

### 2024-02-15 scripts/01-data_cleaning.R

@@ -79,9 +79,11 @@ cleaned_data <- cleaned_data |>
 
 merged_data <- merge(state, cleaned_data, by.x = "region", by.y = "stname", all.x = TRUE)
 
+merged_data_cleaned <- select(merged_data, -subregion)
+
 # Write to CSV
 write_csv(
-  x = merged_data,
+  x = merged_data_cleaned,
   file = "outputs/data/figure_3.csv"
 )
 

### 2024-02-15 scripts/02-test_data.R

@@ -11,60 +11,50 @@ library(tidyverse)
 
 
 #### Test data ####
-# Load dataset
-cleaned_toronto_crime_rates <- read.csv("inputs/data/cleaned_toronto_crime_rates.csv", check.names = FALSE)
-summary_table <- read.csv("inputs/data/summary_table.csv", check.names = FALSE)
-two_types_crime <- read.csv("inputs/data/two_types_crime.csv", check.names = FALSE)
 
-# Test 1: Check for missing values for cleaned_toronto_crime_rates
-test1_result <- !any(is.na(cleaned_toronto_crime_rates))
+# Load dataset
+figure_1 <- read.csv("outputs/data/figure_1.csv", check.names = FALSE)
+figure_2 <- read.csv("outputs/data/figure_2.csv", check.names = FALSE)
+figure_3 <- read.csv("outputs/data/figure_3.csv", check.names = FALSE)
+figure_4 <- read.csv("outputs/data/figure_4.csv", check.names = FALSE)
+table_2 <- read.csv("outputs/data/table_2.csv", check.names = FALSE)
+
+# Test 1: Check for missing values for figure_1
+test1_result <- !any(is.na(figure_1))
 print(paste("Test 1 Passed:", test1_result))
 
-# Test 2: Check for duplicated rows for cleaned_toronto_crime_rates
-test2_result <- !any(duplicated(cleaned_toronto_crime_rates))
+# Test 2: Check for missing values for figure_2
+test2_result <- !any(is.na(figure_2))
 print(paste("Test 2 Passed:", test2_result))
 
-# Test 3: Check the number of columns for summary_table
-expected_num_cols <- 11
-test3_result <- ncol(summary_table) == expected_num_cols
+# Test 3: Check for missing values for figure_3
+test3_result <- !any(is.na(figure_3))
 print(paste("Test 3 Passed:", test3_result))
 
-# Test 4: Check the number of rows for summary_table
-expected_num_rows <- 9
-test4_result <- nrow(summary_table) == expected_num_rows
+# Test 4: Check for missing values for figure_4
+test4_result <- !any(is.na(figure_4))
 print(paste("Test 4 Passed:", test4_result))
 
-# Test 5: Check for missing values for summary_table
-test5_result <- !any(is.na(summary_table))
+# Test 5: Check for missing values for table_2
+test5_result <- !any(is.na(table_2))
 print(paste("Test 5 Passed:", test5_result))
 
-# Test 6: Check for duplicated rows for summary_table
[…]

### 2024-02-15 replications/scripts/fig3_replication.R
Finalize the paper

@@ -7,9 +7,6 @@
 
 
 #### Workspace setup ####
-# install.packages("ggprism")
-# install.packages("ggthemes")
-
 library(tidyverse)
 
 
@@ -19,8 +16,9 @@ library(tidyverse)
 ## Figure 3 ##
 
 # Read in the raw data
-figure3 <- read.csv(here::here("outputs/data/figure_3a.csv"))
+figure3 <- read.csv(here::here("outputs/data/figure_3.csv"))
 
+# Make Plot
 ggplot(figure3, aes(x = long, y = lat, group=group)) +
   geom_polygon(aes(fill = brate1544_thsnds_ch_pct)) +
   scale_fill_gradient(low = 'darkred', high = '#FFCCCB') +
@@ -28,6 +26,7 @@ ggplot(figure3, aes(x = long, y = lat, group=group)) +
        fill = 'Change in Birth Rate') +
   theme_void()
 
+# Save Plots
 ggsave(
   "replication/plots/figure3.png"
 )

### 2024-02-15 scripts/00-simulate_data.R

@@ -41,7 +41,7 @@ simulated_data$Younger <- simulated_data |>
   ) |>
   rowMeans()
 
-simulated_data$Elder <- simulated_data |>
+simulated_data$Older <- simulated_data |>
   select(
     br_3034,br_3539,br_4044
   ) |>

### 2024-02-15 replications/scripts/fig1_replication.R
Finalize the structure

@@ -62,7 +62,7 @@ fig1_data %>%
 
 # Save plot
 ggsave(
-  "replication/plots/figure1.png",
+  "replications/plots/figure1.png",
   height = 100,
   width = 133.33,
   units = "mm",

### 2024-02-15 replications/scripts/fig2_replication.R

@@ -79,7 +79,7 @@ fig_2a_data %>%
 
 # Save plot
 ggsave(
-  "replication/plots/figure2.png",
+  "replications/plots/figure2.png",
   height = 100,
   width = 133.33,
   units = "mm",

### 2024-02-15 replications/scripts/fig3_replication.R

@@ -28,5 +28,5 @@ ggplot(figure3, aes(x = long, y = lat, group=group)) +
 
 # Save Plots
 ggsave(
-  "replication/plots/figure3.png"
+  "replications/plots/figure3.png"
 )

### 2024-02-15 outputs/paper/paper.qmd
Finalize the paper

@@
 #| label: tbl-young-old-br
-#| tbl-cap: First Ten Rows of Birth Rates For Younger and Older Groups Spanning from 1980 to 2020
+#| tbl-cap: First Ten Rows of Birth Rates For Younger and Older Groups from 1980 to 2020
 #| echo: false
@@
                  color = "black", angle = 90, vjust = -0.5) +
-        labs(title = "Birth Rate in America overtime",
-            x = "Years",
+        labs(x = "Years",
             y = "Birth rate") +
@@
            color = "black", angle = 90, vjust = -0.5) +
-  labs(title = "Birth Rate by Age Group Over Time",
-       x = "Year",
+  labs(x = "Year",
        y = "Birth Rate") +
@@
 
-## Birth Rate Comparison between Young and Old Population
+## Birth Rate Comparison between Younger and Older Population
 ```{r}
 #| label: fig-birth-rate-comparison-old-and-young
-#| fig-cap: Birth Rate between Young and Old Population
+#| fig-cap: Birth Rate between Younger and Older Population
 #| echo: false
@@
            color = "black", angle = 90, vjust = -0.5) +
-  labs(title = "Birth Rate between Young and Old Population",
-       x = "Year",
+  labs(x = "Year",
        y = "Birth Rate") +
@@
   scale_fill_gradient(low = 'darkred', high = '#FFCCCB') +
-  labs(title = 'Change in Birth Rate by State Over Time',
-       fill = 'Change in Birth Rate') +
+  labs(fill = 'Change in Birth Rate') +
   theme_void()
@@
 
-## Weaknesses
+## Weaknesses and Future Research Directions
 
@@
 Additionally, the original study did not account for the influence of the Affordable Care Act and its potential impact on family planning decisions, an area our study also does not explore.
-
-## Future Research Directions
 

### 2024-02-22 outputs/paper/paper.qmd
Update paper.qmd

@@
 The younger age group is represented by blue line and the older age group is represented by red line.
-It is evident from the @fig-birth-rate-comparison-old-and-young that the younger age group is higher than that for the old population across the entire time span.
+It is evident from @fig-birth-rate-comparison-old-and-young that the younger age group is higher than that for the old population across the entire time span.
 However, it is also evident that there is a significant birth rate decrease in the young population after 2007, while older population maintains a slowly increasing trend.
@@
 ```
-We then shift our focus to geographical variations in birth rates across states, presented in @fig-change-in-birth-rates-by-state.
-The graph portrays the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
+We then shift our focus to geographical variations in birth rates across states [@fig-change-in-birth-rates-by-state].
+The illustrates the change in birth rates by state across the United States over the period from 2004–2008 to 2015–2019, avoiding the immediate effects of the Great Recession by focusing on the periods before and after its main impact.
 The map's color gradient, which darkens with more significant decreases in birth rates, shows substantial variation across states.
@@
 
-# References
+\appendix
 
-::: {#refs}
-:::
+# Appendix {-}
 
-{{< pagebreak >}}
+# Data Manipulation and Cleaning {#sec-appendix}
 
-# Appendix {#sec-appendix}
-## Data Manipulation and Cleaning
 Most of the data in our dataset was previously cleaned for the project we are replicating.
-Thus, figure 1 directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary, as it simply displays the birth rate from 1980 to 2020.
+Thus, @fig-trends-in-birth-rate directly used data from `outputs/data/fig_1.csv` without any further cleaning necessary, as it simply displays the birth rate from 1980 to 2020.
 Thus, the cleaned data is directly stored to `outputs/data/fig_1.csv` from `inputs/data/fig_1.csv`.
 
-In figure 2, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr`[@citedplyr] to select the birth rates of the six age groups (from 15 to 44).
-Furthermore, the selected data was renamed using `tidyverse`[@citetidyverse] and changed into names that represent the content of the data better.
-Moreover, these data is then pivoted using `tidyverse`[@citetidyverse] in order to be graphed properly using `ggplot2`[@citeggplot].
+In @fig-trends-in-birth-rate-in-young-people, the dataset was imported from `inputs/data/fig_2.csv` and used `dpylr` [@citedplyr] to select the birth rates of the six age groups (from 15 to 44).
+Furthermore, the selected data was renamed using `tidyverse` [@citetidyverse] and changed into names that represent the content of the data better.
+Moreover, these data is then pivoted using `tidyverse` [@citetidyverse] in order to be graphed properly using `ggplot2` [@citeggplot].
 
-In figure 3, the first dataset was imported from `inputs/data/fig_3.csv` and the dataset containing American states information was from `mapdata` [@citemapdata].
+In @fig-birth-rate-comparison-old-and-young, the first dataset was imported from `inputs/data/fig_3.csv` and the dataset containing American states information was from `mapdata` [@citemapdata].
 The first dataset was first sliced to remove birth rate information regarding the states of Alaska and Hawaii, as these two states can't be properly shown in the dataset from `mapdata` [@citemapdata].
-Then, a temporary data frame is created with tibble from `tidyverse`[@citetidyverse] with the abbreviated state names from `inputs/data/fig_3.csv` and the state full names.
-Moreover, the abbreviated state name in the first dataset is switched with the state full name using left_join from `dpylr`[@citedplyr], which is then selected and renamed using `tidyverse`[@citetidyverse].
-After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven`[@citehaven].
+Then, a temporary data frame is created with tibble from `tidyverse` [@citetidyverse] with the abbreviated state names from `inputs/data/fig_3.csv` and the state full names.
+Moreover, the abbreviated state name in the first dataset is switched with the state full name using left_join from `dpylr` [@citedplyr], which is then selected and renamed using `tidyverse` [@citetidyverse].
+After this, the adjusted dataset with the state full names and birth rate is merged with the second dataset that contains the American states information for further graphing with `haven` [@citehaven].
 
 In all three figures, the library `here` [@citehere] was used to ensure that the file path should be accessible in all directories.
+
+\newpage
+
+# References
